---
title: "Briggsdale"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---
# Setup
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
## load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library(plotly)
#library(fs)
library(gridExtra)
library(egg)
library(readxl)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

```{r load data}
tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))

soil_temps_july <- tibble(
  Flask = c(3:16),
  Temp_C = c(25.1,23.0,22,25.9,23.6,22,24.3,23.0,22,23.4,22.4,22, 24.0,22.9)
)

soil_temps_October <- tibble(
  Flask = c(2:13),
  Temp_C = c(23.3,21.8,20.55,16.7,19.0,19.3,18.9,18.9,18.8,15.56,16.0,16.9),
  sampledate = c(
    "2022-09-18","2022-09-18","2022-09-18",
    "2022-09-24","2022-09-24","2022-09-24",
    "2022-09-30","2022-09-30","2022-09-30",
    "2022-10-06","2022-10-06","2022-10-06")
)
  
```
October data:
*I estimated the 25 cm temperature with 15 cm data from CoAgMet. 
*I estimated the 50 cm temperature manually. 

From the data logger:  
75 cm: 
9-18-22: 20.55°C, 
9-24-22: 19.3°C, 
9-30-22: 18.8°C, 
10-6-22: 16.9°C, 
10-12-22: 16.1°C



# First deployment
## August 10, 2022

Flask 16: 13:33-13:44
Flask 15: 14:12-14:22
Flask 14: 15:11-15:21 batch 102
DI-080222: 15:45-16:14
DI-080222: 16:17-16:25
Flask 13: 16:50-17:00 - batch 329
Flask 12: 17:14-17:24 - batch 359
Flask 11: 17:36 - 17:46 - batch 388

March 20, 2023 -> batch numbers don't seem to work, not sure why, so re-doing batch filtering. something funky with timezones is happening, needed to adjust filter by one hour 

```{r}
data_0810 <- tbl %>% 
  filter (DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-10 12:30" & MDT < "2022-08-10 18:00") %>% 
  h2o_batches() %>% 
  filter (H2O_Batch == 22 | H2O_Batch == 46 | H2O_Batch == 102 | H2O_Batch == 329 | H2O_Batch == 359 | H2O_Batch == 388)

h2o_batch_plt(data_0810)
d180_time_plt(data_0810)
h2O_FirstThreeMinutes(data_0810)

flasks_0810 <- data_0810 %>% 
  flask_first3minutes() %>% 
  mutate(
    Flask = c(16:11),
    sampledate = ifelse(Flask > 13, "2022-08-06", "2022-08-01"),
    sampledepth = c(75,50,25,75,50,25),
    Analyst = "Haley"
  )
```




## August 11 

flask 10, 11:10 - 11:20
flask 9: 11:41- 11:51
Flask 8: 12:16-12:27
flask 7: 12:45 - 12:56
flask 6: 13:19-13:30
flask 5: 14:03-14:13

```{r}
data_0811 <- tbl %>% 
  filter(DATE == "2022-08-11") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-11 10:00" & MDT < "2022-08-11 13:13:30") %>% 
  h2o_batches() %>% 
  filter(H2O >5000)

h2o_batch_plt(data_0811)
h2O_FirstThreeMinutes(data_0811)

flasks_0811 <- data_0811 %>% 
  flask_first3minutes() %>% 
  mutate(
    Flask = c(10:5),
    sampledate = ifelse (Flask >7 & Flask < 11, "2022-07-27", "2022-07-22"),
    sampledepth = c(75,50,25,75,50,25),
    Analyst = "Haley"
  )
```

## August 12, 2022
```{r}
data_0812 <- tbl %>% 
  filter(DATE == "2022-08-12") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-12 11:21" & MDT < "2022-08-12 12:53") %>% 
  h2o_batches() %>% 
  filter(H2O > 5000)

h2o_batch_plt(data_0812)
d180_time_plt(data_0812)
h2O_FirstThreeMinutes(data_0812)

flasks_0812 <- data_0812 %>% 
  flask_first3minutes() %>% 
    mutate(
        Flask = c(4:2),
        sampledate = "2022-07-17",
        sampledepth = c(75,50,25),
        Analyst = "Haley"
    )
```


## Correct July Data
1. Add in the column of soil temperature data
2. Using soil temp, convert vapor values to liquid water values
3. Using the 08/22 Calibration from the calibrations.rmd. 
d18O_corr = (d18O_liq - 0.3336484) / 1.0072042. 
d2H_corr = (d2H_liq - -7.408711) / 1.008137. 
4. Apply the SWISS offset correction 
```{r}
Brigssdale_july2022 <- bind_rows(flasks_0810,flasks_0811,flasks_0812) %>% 
  left_join(soil_temps_july, by = "Flask") %>% 
  liq_rothfuss2013() %>% 
  mutate(
    d18O_corr = round( ((d18O_liq - 0.3336484) / 1.0072042),1),
    d2H_corr = round( ((d2H_liq - -7.408711) / 1.008137), 1)) %>% 
  SWISS_offset ()
```



```{r}
Brigssdale_july2022_plt <- Brigssdale_july2022 %>%   
  filter(sampledepth > 25) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Briggsdale, CO")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18O_offset - 0.9,
    ymin = d18O_offset + 0.9,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18O_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(23,24), name = "Sample Depth (cm)") +
  scale_fill_manual(values = c("#20908C", "#FCE621"), name = "Sample Depth (cm)")+
  theme_figure() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )

Brigssdale_july2022_plt
```

```{r}
Brigssdale_d2h <- Brigssdale_july2022 %>% 
  filter(sampledepth > 25) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  geom_errorbar(aes(
    x = sampledate,
    ymax = dD_offset - 3.6,
    ymin = dD_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = dD_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(23,24), name = "Sample Depth (cm)") +
  scale_fill_manual(values = c("#20908C", "#FCE621"), name = "Sample Depth (cm)")+
  theme_figure() +
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(Brigssdale_d2h)
```

```{r Briggsdale june data}
ggarrange(Brigssdale_july2022_plt, Brigssdale_d2h)

Brigssdale_july2022 %>% 
  filter(sampledepth > 25) %>% 
  mutate(
    Site = "Briggsdale"
  ) %>% 
    dplyr::select(Site, sampledate, sampledepth, Flask, Temp_C, d18O_offset, SD_18O_out, dD_offset, SD_2H_out) %>% 
      arrange(Flask) %>% 
        rename(Date = sampledate, Depth = sampledepth, AnalyticalError = SD_18O_out) %>% 
        write.csv("output/BriggsdaleJulyData.csv")
```


```{r}
crossplt <- Brigssdale_july2022 %>% 
  filter(sampledepth > 25) %>% 
  ggplot()+
  geom_abline(intercept = 10, slope = 8, size = 2, linetype = "longdash")+
  geom_errorbar(aes(
    x = d18O_offset,
    ymax = dD_offset - 3.6,
    ymin = dD_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = dD_offset,
    xmax = d18O_offset - 0.9,
    xmin = d18O_offset + 0.9,
    height = 0)) +
  geom_point(
    aes(
      x = d18O_offset, 
      y = dD_offset, 
      pch = factor(sampledepth),
      fill = factor(sampledate)),
    size = 6
  )+
  scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  #scale_x_continuous(limits = c(-15, -7))+
  #scale_y_continuous(limits = c(-80, -50))+
  theme_figure()

crossplt
```

```{r}
B_dexcess <- Brigssdale_july2022 %>% 
  #filter(sampledepth > 25) %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22, 23, 24), name = "Sample Depth (cm)") +
  #scale_fill_manual(values = c("#20908C", "#FCE621"), name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(B_dexcess)
```

```{r}
write.csv(Brigssdale_july2022, "output/BriggsdaleResults_July2022.csv")
```




# October 2022
Measured flasks in order 16 -> 2. Flasks 16, 15, 14 didn't have a signal because the dry air tank had emptied itself 
Exclude flask 7 -> the measurement was very variable. Time window matters too much
Exclude flask 5, drifts 1.5 per mil over the first 3 minutes

Its not surprising to me that the data from 09-24-22 were bad -> there was a cold snap on the 22-23. There is definitely something in conditions during sampling effecting how well a sample comes out. Its most pronounced in the Siebert samples. 


filter data between 9 am and 6 pm mountain time
```{r}
Oct22 <- tbl %>% filter(DATE == "2022-10-17" | DATE == "2022-10-18") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-10-17 08:00" & MDT < "2022-10-17 17:00") %>% 
  h2o_batches()

#check out the data
h2o_batch_plt(Oct22)

Oct22 %>% 
  filter(MDT> "2022-10-17 11:05" & MDT < "2022-10-17 15:30") %>% 
  filter(H2O > 5000) %>% 
    d18O_three_minute_start()

#this one looks bad 
flask7_Oct22 <- Oct22 %>% 
  filter(MDT > "2022-10-17 13:40:30" & MDT < "2022-10-17 13:53") %>% 
  d180_time_plt()

#pull together data
flasks_Oct22 <-  Oct22 %>% 
  filter(MDT> "2022-10-17 11:05" & MDT < "2022-10-17 15:30") %>% 
  filter(H2O > 5000) %>% 
  filter(H2O_Batch != 460) %>% #excludes flask 7
  filter(H2O_Batch != 549) %>% # excludes flask 5
  flask_first3minutes() %>% 
  mutate(
    Flask = c(13:8,6,4,3,2)
  ) %>% 
  left_join(soil_temps_October, by = "Flask") %>% 
  liq_rothfuss2013() %>% 
  mutate(
    d18O_vsmow = (d18O_liq - 0.711) / 1.018,
    d2H_vsmow = (d2H_liq - -0.4566) / 1.0297,
    
    d18o_offset =  round(d18O_vsmow - 0.9, 1),
    d2H_offset =  round(d2H_vsmow - 2.6,1),
    
    dexcess = d2H_offset - 8*d18o_offset,
    SWISS = "Lindt",
    site = "Briggsdale",
    sampledepth = c(75,50,25,75,50,25,50,75,50,25)
  )
```



```{r}
Briggsdale_d18o_22 <- flasks_Oct22 %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Briggsdale, CO")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18o_offset - 1.0,
    ymin = d18o_offset + 1.0,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18o_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )
  

print(Briggsdale_d18o_22)


Brigssdale_d2h_22 <- flasks_Oct22 %>% 
  filter(sampledate < "2022-10-10") %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
  )

print(Brigssdale_d2h_22)


Briggsdale_dexcess_22 <- flasks_Oct22 %>% 
  filter(sampledate < "2022-10-10") %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = dexcess + 3.5,
    ymin = dexcess - 3.5,
    width = 0
  )) + 
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(Briggsdale_dexcess_22)


ggarrange(Briggsdale_d18o_22,Brigssdale_d2h_22,Briggsdale_dexcess_22)
```


```{r}
Brigssdale_july <- Brigssdale_july2022 %>% 
  rename(
    d18O_vsmow = "d18O_corr",
    d2H_vsmow = "d2H_corr",
    d18o_offset = "d18O_offset",
    d2H_offset = "dD_offset"
  ) %>% 
  filter(sampledepth != 25)

#Brigssdale_july2022$sampledate <- as.Date(Brigssdale_july2022$sampledate)



allB <- bind_rows(Brigssdale_july, flasks_Oct22)

crossplt_all <- allB %>% 
  
  ggplot()+
  geom_abline(intercept = 10, slope = 8, size = 1, linetype = 3)+
    geom_abline(intercept = -1.543251, slope = 7.523888, size = 1, linetype = 1 ) +
  geom_errorbar(aes(
    x = d18o_offset,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = d2H_offset,
    xmax = d18o_offset - 0.9,
    xmin = d18o_offset + 0.9,
    height = 0)) +
  geom_point(
    aes(
      x = d18o_offset, 
      y = d2H_offset, 
      pch = factor(sampledepth),
      color = factor(sampledate)),
    size = 6
  )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  theme_figure()

crossplt_all


```

Note to Rachel: add in the clumped box

```{r}
precip1 <- read_csv("data/Precipitation_data/Near Briggsdale Isomap Precip.csv")
precip2 <- read_csv("data/Precipitation_data/NEON_Briggsdale_precip.csv")

precip <- bind_rows(precip1, precip2) %>% 
  mutate(month = month(Collection_Date))

SW_precip <- allB %>% 
  ggplot()+
  annotate("rect", xmax = -8.6, xmin = -10.2, ymax =40, ymin = -200, alpha = 0.5, fill = "#40ADD3") + 
  #Meteoric water lines and precipitation
    geom_abline(intercept = 10, slope = 8, size = 1, linetype = 3)+
    geom_abline(intercept = -1.543251, slope = 7.523888, size = 1, linetype = 1 ) +
    geom_point(data = precip, aes(x = d18O, y = d2H, fill = month),shape = 24 ) +
    scale_fill_viridis(option = "turbo") +

  #Soil Water data
    
    geom_errorbar(aes(
      x = d18o_offset,
      ymax = d2H_offset - 3.6,
      ymin = d2H_offset + 3.6,
      width = 0)) +
    geom_errorbarh(aes(
      y = d2H_offset,
      xmax = d18o_offset - 0.9,
      xmin = d18o_offset + 0.9,
      height = 0)) +
    geom_point(
      aes(
        x = d18o_offset, 
        y = d2H_offset, 
        pch = factor(sampledepth),
        color = factor(sampledate)),
      size = 5
    )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  scale_y_continuous(limits = c(-200, 40), expand = c(0,0))+
  scale_x_continuous(limits = c(-25, 5), expand = c(0,0))+
  theme_figure()

SW_precip


SW_precip2  <- allB %>% 
  ggplot()+
  annotate("rect", xmax = -8.6, xmin = -10.2, ymax =40, ymin = -200, alpha = 0.5, fill = "#40ADD3") +
  #Meteoric water lines and precipitation
    geom_abline(intercept = 10, slope = 8, size = 1, linetype = 3)+
    geom_abline(intercept = -1.543251, slope = 7.523888, size = 1, linetype = 1 ) +
    geom_point(data = precip, aes(x = d18O, y = d2H,), shape = 23, fill = "#cecece" ) +
    

  #Soil Water data
    
    geom_errorbar(aes(
      x = d18o_offset,
      ymax = d2H_offset - 3.6,
      ymin = d2H_offset + 3.6,
      width = 0)) +
    geom_errorbarh(aes(
      y = d2H_offset,
      xmax = d18o_offset - 0.9,
      xmin = d18o_offset + 0.9,
      height = 0)) +
    geom_point(
      aes(
        x = d18o_offset, 
        y = d2H_offset, 
        pch = factor(sampledepth),
        color = factor(sampledate)),
      size = 5
    )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  scale_y_continuous(limits = c(-200, 40), expand = c(0,0))+
  scale_x_continuous(limits = c(-25, 5), expand = c(0,0))+
  theme_figure()

SW_precip2

```






```{r}
finaltbl <- allB %>% 
  mutate(site = "Briggsdale") %>% 
  dplyr::select(
    site, 
    sampledate,
    sampledepth,
    d18o_offset,
    d2H_offset,
    dexcess
  ) %>% 
  arrange(sampledate, sampledepth) %>% 
  rename(
    "Site" = site,
    "Sample Date" = sampledate,
    "Sample Depth (cm)" = sampledepth,
    "d18O (VSMOW)" = d18o_offset,
    "d2H (VSMOW)" = d2H_offset,
    "d-excess ()" = dexcess
  )

write.csv(finaltbl, "output/BriggsdaleResults_ch3.csv")
```











