---
title: "Calibrations"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---
The purpose of this markdown is to provide a place to do the data reduction on the vapor calibrations. 

#Set up 
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(dplyr)
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     as_tibble() %>%
#     dplyr::select(1, 2, 15, 17, 18, 19)
# 
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Standard values
```{r}
stds <- tibble(
  std = c("KFW", "KBW", "KAW", "KGW"),
  d18o_known = c(-0.76, -14.15, -30.30, -38.02),
  d2H_known = c(-2.82,-111.65,-239.13, -298.37),
  type = "known"
)
```

# March 18, 2022 calibration
Julien 
```{r}
data_031822 <- tbl %>% 
  filter(DATE == "2022-03-18" | DATE == "2022-03-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-18 12:00:00" & MDT < "2022-03-19 02:15:00")

d180_time_plt(data_031822)
waterConcentration_plt(data_031822)

KFW_031822 <- data_031822 %>% 
  filter(MDT >"2022-03-18 16:10:00" & MDT < "2022-03-18 17:00:00") %>% 
  flask_out_ave() %>% mutate (std = "KFW")


KAW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 18:45:00" & MDT < "2022-03-18 19:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 21:20:00" & MDT < "2022-03-18 21:50:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_031822 <- data_031822 %>% filter(MDT > "2022-03-18 23:55:00" & MDT < "2022-03-19 00:20:00") %>% flask_out_ave() %>% mutate(std = "KBW")


observed_stds <- bind_rows(KFW_031822, KAW_031822, KGW_031822, KBW_031822) %>% 
  mutate(
    type = "Observed"
  )

all <- full_join(observed_stds, stds, by = "std")

all %>% ggplot()+
  aes(x = d18o_known, y = d18O_out)+
  geom_point()+
   geom_line()

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all)
dD_lm <- lm(d2H_out ~ d2H_known, all)

#double check it worked
all <- all %>% 
  mutate(
    d18O_iso_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_iso_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )


print(d18O_lm$coefficients[1])
print(d18O_lm$coefficients[2])

write.csv(data_031822, "data_031822.csv")
```
## Equations transfered into corrections script
d18O_corr = (d18O_out - 1.68206) / 1.026412
d2H_corr = (d2H_out - 5.669731) / 1.045704


# April 3, 2022 Calibration 
Julien 
```{r}
data_040422 <- tbl %>% 
  filter(DATE == "2022-04-04" | DATE == "2022-04-05") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

#waterConcentration_plt(data_040422)

KFW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422 <- bind_rows(KFW_040422, KAW_040422, KGW_040422, KBW_040422) %>% 
  full_join(stds, by = "std")

stds_plt <- stds_040422 %>% 
  ggplot()+
    aes(x = d18o_known, y = d18O_out)+
    geom_point()+
    geom_line()

d18O_lm_0404 <- lm(d18O_out ~ d18o_known, stds_040422)
dD_lm_0404 <- lm(d2H_out ~ d2H_known, stds_040422)

stds_040422 <- stds_040422 %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404$coefficients[1])/d18O_lm_0404$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404$coefficients[1])/dD_lm_0404$coefficients[2],
  )
```

## Equations copied into corrections script
d18O_corr = (d18O_out - 1.4572)/1.0281
d2H_corr = (d2H_out - 5.595052)/1.046536


#April 4 on Phlox
```{r}
phlox0404 <- 
    list.files ("data/Phlox_April4", pattern = "*.dat", recursive = T, full.names = T) %>%
    map_df(~read_table2(.)) %>%
    as_tibble() %>%
    dplyr::select(1, 2, 15, 17, 18, 19)

phlox0404 <- phlox0404 %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

waterConcentration_plt(phlox0404)

KFW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422_phlox <- bind_rows(KFW_040422_phlox, KAW_040422_phlox, KGW_040422_phlox, KBW_040422_phlox) %>% 
  full_join(stds, by = "std")


d18O_lm_0404_phlox <- lm(d18O_out ~ d18o_known, stds_040422_phlox)
dD_lm_0404_phlox <- lm(d2H_out ~ d2H_known, stds_040422_phlox)


stds_040422_phlox <- stds_040422_phlox %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404_phlox$coefficients[1])/d18O_lm_0404_phlox$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404_phlox$coefficients[1])/dD_lm_0404_phlox$coefficients[2],
  )

stds_040422_phlox <- stds_040422_phlox %>% April4_phlox_corr()

```

d18O_corr_phlox = (d18O_out - 4.229)/1.045868
d2H_corr_phlox = (d2H_out + 0.00710443)/1.050112

# July 2022
## July 19, 2022
On July 19 and 20 we (Haley) ran three standards, ygrette4, DI from benson, and a heavy water. All of those were subsampled for discrete runs. As of august 16, 2022 they haven't been run yet, but I expect to do that run the first week of September. 

On july 19
There were probably large room temp fluctuations while Haley ran the last heavy standard. If you look at the first 10 minutes, d18O centers around -12.5 per mil, but from 16:25 - 16:33 it cetners morre around - 11.9. I chose to keep the lighter value, since that is more likely in line with the values from the other standards temperature wise. I've kept the plot of the fluctuating values for reference. 

the very last one is a little funky and shows some 'bowing' 
```{r}
data_071922 <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-07-19 14:30:00" & MDT < "2022-07-19 16:40") %>% 
        h2o_batches()

h2o_batch_plt(data_071922)
d180_time_plt(data_071922)
h2O_FirstThreeMinutes(data_071922)

manualHeavy <- data_071922 %>% 
  filter(MDT >"2022-07-19 16:10" & MDT < "2022-07-19 16:37")

waterConcentration_plt(manualHeavy)
d180_time_plt(manualHeavy)

stds_071922 <- data_071922 %>% 
  filter(H2O_Batch == 0 | H2O_Batch == 106 | H2O_Batch == 247) %>% 
    flask_first3minutes() %>% 
     mutate(
       StdName = c("Ygrette4", "Ygrette4", "Heavy"),
       T = 27,
       Analyst = "Haley",
     )
```

## July 20, 2022 

```{r}
data_072022 <- tbl %>% 
  filter (DATE == "2022-07-20") %>% 
    BoulderTime() %>% 
      filter (MDT > "2022-07-20 12:45:00" & MDT < "2022-07-20 15:15") %>% 
        h2o_batches()

waterConcentration_plt(data_072022)
h2o_batch_plt(data_072022)
h2O_FirstThreeMinutes(data_072022 %>% filter (H2O_Batch>1))
d180_time_plt(data_072022)

stds_072022 <- data_072022 %>% 
  filter (H2O_Batch>1) %>% 
  flask_first3minutes() %>% 
  mutate(
    StdName = c("Heavy", "Heavy", "DI", "DI"),
       T = 27,
       Analyst = "Haley"
  )
```


```{r}
julystd <- bind_rows(stds_071922, stds_072022) %>% 
  ggplot()+
  aes(x = d18O_out, y = d2H_out, color= StdName)+
  geom_errorbar(aes(ymin = d2H_out - 2, ymax = d2H_out + 2))+
  geom_errorbarh(aes(xmin = d18O_out - 0.5, xmax = d18O_out + 0.5))+
  geom_point()

print(julystd )
```

# August 2022
Between August 5 - 12 we measured two SWISS pulled from the field, and so we also tried to measure our own standards in the meantime. Additionally, I tried to do a 'valco' run using the vaporizer system, but that run was unsuccessful. For these, we have some new standards:
* Benson DI 080222 -> BDI_080222
* Heavy #2 080322 -> H2_080322
* Light 8/3/22 #1 -> L1_080322 

## August 5, 2022
```{r}
data_080522 <- tbl %>% 
  filter(DATE == "2022-08-05") %>% 
    BoulderTime() %>% 
      filter (MDT > "2022-08-05 14:42" & MDT < "2022-08-05 15:30") %>% 
        h2o_batches()

waterConcentration_plt(data_080522)
h2o_batch_plt(data_080522)
h2O_FirstThreeMinutes(data_080522)

stds_080522 <- data_080522 %>% 
  filter (H2O_Batch != 54) %>% 
  flask_first3minutes() %>% 
  mutate(
    StdName = c("DI", "Ygrette4"),
       T = 27,
       Analyst = "Haley"
  )
```

## August 9, 2022 probe stds
12:30 - 4:00
2 x ygrette4
  The first ygrette has a definite trend. Going to do that one by hand 

2 x BDI0800322
2 x Heavy2_080322

```{r}
data_080922 <- tbl %>% 
  filter (DATE == "2022-08-09") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-08-09 12:00" & MDT < "2022-08-09 16:00") %>% 
  h2o_batches()

ygrette <- data_080922 %>% 
  filter (MDT >"2022-08-09 12:45" & MDT < "2022-08-09 12:50") %>% 
  flask_out_ave() %>% 
  mutate(
     StdName = c("Ygrette4"),
     T = 27,
     Analyst = "Haley"
  )


h2o_batch_plt(data_080922 %>% filter(H2O_Batch >179))
d180_time_plt(data_080922 %>% filter(H2O_Batch >179))
h2O_FirstThreeMinutes(data_080922 %>% filter(H2O_Batch >179 & H2O > 15000))

stds_080922 <- data_080922 %>% 
  filter(H2O_Batch >179 & H2O > 15000) %>% 
  flask_first3minutes() %>% 
  mutate(
     StdName = c("Ygrette4", "BDI_080222", "BDI_080222", "BDI_080222", "H2_080322", "H2_080322"),
     T = 27,
     Analyst = "Haley"
  ) %>% 
  bind_rows(ygrette)
```

## August 9 2022 vaporizer 
- Phlox 
- Started at approx. 17:54:00 

- well this calibration didn't work. The python code seems to have gotten stuck, and it didn't swap away from port 2 on the valco. 
```{r}
data_080922 <- tbl %>% 
  filter(DATE == "2022-08-09" | DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-08-09 17:45:00" & MDT < "2022-08-09 20:00:00")

waterConcentration_plt(data_080922)
d180_time_plt(data_080922)
```

## August 10 
```{r}
firstround_081022 <- tbl %>% 
  filter (DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-10 10:47" & MDT < "2022-08-10 12:00") %>% 
  h2o_batches()

h2o_batch_plt(firstround_081022)
h2O_FirstThreeMinutes(firstround_081022)

stds_081022 <- firstround_081022 %>% 
  filter(H2O > 5000) %>% 
  flask_first3minutes() %>% 
  mutate(
    StdName = c("Ygrette4", "BDI_080222"),
     T = 27,
     Analyst = "Haley"
  )

secondbatch <- firstround_081022 <- tbl %>% 
  filter (DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
    filter(MDT > "2022-08-10 16:00" & MDT < "2022-08-10 16:26") %>% 
      h2o_batches() %>% 
        flask_first3minutes() %>% 
        mutate(
          StdName = c("BDI_080222", "BDI_080222"),
          T = 23,
          Analyst = "Haley"
  )


stds_081022 <- stds_081022 %>% 
  bind_rows(secondbatch)
```


## August 11
```{r}
data_081122 <- tbl %>% 
  filter (DATE == "2022-08-11") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-11 9:30") %>% 
        h2o_batches() %>% 
          filter(H2O_Batch == 68 | H2O_Batch == 134 | H2O_Batch == 399 | H2O_Batch == 482 | H2O_Batch == 564)

h2o_batch_plt(data_081122)
d180_time_plt(data_081122)

stds_081122 <- data_081122 %>% 
  flask_first3minutes() %>% 
    mutate(
      StdName = c("BDI_080222", "BDI_080222", "BDI_080222", "L1_080322", "H2_080322"),
          T = 23,
          Analyst = "Haley"
    )
```

## August 12 
```{r}
data_081222 <- tbl %>% 
  filter(DATE == "2022-08-12") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-12 10:20" & MDT < "2022-08-12 15:15") %>% 
        h2o_batches() %>% 
          filter(H2O_Batch == 51 | H2O_Batch == 126 | H2O_Batch ==206 | H2O_Batch == 463  | H2O_Batch == 623)



batch545 <- tbl %>% 
  filter(DATE == "2022-08-12") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-12 14:39:00" & MDT < "2022-08-12 14:42:01") %>% flask_out_ave() %>% 
        mutate(
          StdName = c("BDI_080222"),
          T = 23,
          Analyst = "Haley")
        

stds_081222 <- data_081222 %>% 
  flask_first3minutes() %>% 
   mutate(
      StdName = c("L1_080322", "BDI_080222", "H2_080322", "L1_080322", "H2_080322"),
          T = 23,
          Analyst = "Haley") %>% 
            bind_rows(batch545)
```

## August 16 
Valco calibration done on the humidity system. one hour seems to be a good amount of time, could maybe be even longer
```{r}
data_081622 <- tbl %>% 
  filter(DATE == "2022-08-16" | DATE == "2022-08-17") %>% 
  BoulderTime() %>% 
  filter(MDT<"2022-08-16 22:03") 

waterConcentration_plt(data_081622)
d180_time_plt(data_081622)

KFW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 17:51" & MDT < "2022-08-16 18:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KFW")

KAW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 18:51" & MDT < "2022-08-16 19:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KAW")

KGW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 19:51" & MDT < "2022-08-16 20:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KGW")

KBW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 20:51" & MDT < "2022-08-16 21:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KBW")

stds_0817 <- bind_rows(KFW_0816, KAW_0816, KGW_0816, KBW_0816)


all_0816 <- full_join(stds_0817, stds, by = "std")

all_0816 %>% ggplot()+
  aes(x = d18o_known, y = d18O_out, size = 2)+
  geom_point()+ 
  geom_smooth(method = "lm", se = FALSE, aes(size = 0.5))

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all_0816)
dD_lm <- lm(d2H_out ~ d2H_known, all_0816)

#double check it worked
all_0816 <- all_0816 %>% 
  mutate(
    d18O_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )

print(d18O_lm$coefficients[1])
print(d18O_lm$coefficients[2])

```

### Equations transfered into corrections script
d18O_corr = (d18O_out - 0.7917232) / 1.02183
d2H_corr = (d2H_out - 2.226) / 1.036

