---
title: "Calibrations"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---
The purpose of this markdown is to provide a place to do the data reduction on the vapor calibrations. 

** Note: Lubridate uses your computer's timezone to do the data filtering (And plots it in the correct timezone). So, the timezone for each of the filters needs to be updated if you are using this code outside of MDT. 

#Set up 
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(dplyr)
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path ("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     as_tibble() %>%
#     dplyr::select(1, 2, 15, 17, 18, 19)
# 
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Standard values
```{r}
stds <- tibble(
  std = c("KFW", "KBW", "KAW", "KGW", "BDI_080222","Ygrette4", "H2_080322", "H072022", "2019DI_Gallon"),
  d18o_known = c(-0.76, -14.15, -30.30, -38.02, -17.02, -25.45, 5.35, -3.43, -15.87),
  d2H_known = c(-2.82,-111.65,-239.13, -298.37, -124.9, -187.5, -49.5, -76.9, -119.7),
  type = "known"
)
```




# March 18, 2022 calibration
Julien 
```{r}
data_031822 <- tbl %>% 
  filter(DATE == "2022-03-18" | DATE == "2022-03-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-18 12:00:00" & MDT < "2022-03-19 02:15:00")

d180_time_plt(data_031822)
waterConcentration_plt(data_031822)

KFW_031822 <- data_031822 %>% 
  filter(MDT >"2022-03-18 16:10:00" & MDT < "2022-03-18 17:00:00") %>% 
  flask_out_ave() %>% mutate (std = "KFW")


KAW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 18:45:00" & MDT < "2022-03-18 19:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 21:20:00" & MDT < "2022-03-18 21:50:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_031822 <- data_031822 %>% filter(MDT > "2022-03-18 23:55:00" & MDT < "2022-03-19 00:20:00") %>% flask_out_ave() %>% mutate(std = "KBW")


observed_stds <- bind_rows(KFW_031822, KAW_031822, KGW_031822, KBW_031822) %>% 
  mutate(
    type = "Observed"
  )

all <- full_join(observed_stds, stds, by = "std")

all %>% ggplot()+
  aes(x = d18o_known, y = d18O_out)+
  geom_point()+
   geom_line()

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all)
dD_lm <- lm(d2H_out ~ d2H_known, all)

#double check it worked
all <- all %>% 
  mutate(
    d18O_iso_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_iso_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )


print(d18O_lm$coefficients[1])
print(d18O_lm$coefficients[2])

write.csv(data_031822, "data_031822.csv")
```
## Equations transfered into corrections script
d18O_corr = (d18O_out - 1.68206) / 1.026412
d2H_corr = (d2H_out - 5.669731) / 1.045704


# April 3, 2022 Calibration 
Julien 
```{r}
data_040422 <- tbl %>% 
  filter(DATE == "2022-04-04" | DATE == "2022-04-05") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

#waterConcentration_plt(data_040422)

KFW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422 <- bind_rows(KFW_040422, KAW_040422, KGW_040422, KBW_040422) %>% 
  full_join(stds, by = "std")

stds_plt <- stds_040422 %>% 
  ggplot()+
    aes(x = d18o_known, y = d18O_out)+
    geom_point()+
    geom_line()

d18O_lm_0404 <- lm(d18O_out ~ d18o_known, stds_040422)
dD_lm_0404 <- lm(d2H_out ~ d2H_known, stds_040422)

stds_040422 <- stds_040422 %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404$coefficients[1])/d18O_lm_0404$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404$coefficients[1])/dD_lm_0404$coefficients[2],
  )
```

## Equations copied into corrections script
d18O_corr = (d18O_out - 1.4572)/1.0281
d2H_corr = (d2H_out - 5.595052)/1.046536


#April 4 on Phlox
```{r}
phlox0404 <- 
    list.files ("data/Phlox_April4", pattern = "*.dat", recursive = T, full.names = T) %>%
    map_df(~read_table2(.)) %>%
    as_tibble() %>%
    dplyr::select(1, 2, 15, 17, 18, 19)

phlox0404 <- phlox0404 %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

waterConcentration_plt(phlox0404)

KFW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422_phlox <- bind_rows(KFW_040422_phlox, KAW_040422_phlox, KGW_040422_phlox, KBW_040422_phlox) %>% 
  full_join(stds, by = "std")


d18O_lm_0404_phlox <- lm(d18O_out ~ d18o_known, stds_040422_phlox)
dD_lm_0404_phlox <- lm(d2H_out ~ d2H_known, stds_040422_phlox)


stds_040422_phlox <- stds_040422_phlox %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404_phlox$coefficients[1])/d18O_lm_0404_phlox$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404_phlox$coefficients[1])/dD_lm_0404_phlox$coefficients[2],
  )

stds_040422_phlox <- stds_040422_phlox %>% April4_phlox_corr()

```

d18O_corr_phlox = (d18O_out - 4.229)/1.045868
d2H_corr_phlox = (d2H_out + 0.00710443)/1.050112

# July 2022
## July 19, 2022
On July 19 and 20 we (Haley & I) ran three standards, ygrette4, DI from benson, and a heavy water. All of those were subsampled for discrete runs. As of august 16, 2022 they haven't been run yet, but I expect to do that run the first week of September. 

On july 19
There were probably large room temp fluctuations while Haley ran the last heavy standard. If you look at the first 10 minutes, d18O centers around -12.5 per mil, but from 16:25 - 16:33 it cetners morre around - 11.9. I chose to keep the lighter value, since that is more likely in line with the values from the other standards temperature wise. I've kept the plot of the fluctuating values for reference. 

the very last one is a little funky and shows some 'bowing' 
```{r}
data_071922 <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-07-19 14:30:00" & MDT < "2022-07-19 16:40") %>% 
        h2o_batches()

h2o_batch_plt(data_071922)
d180_time_plt(data_071922)
h2O_FirstThreeMinutes(data_071922)

manualHeavy <- data_071922 %>% 
  filter(MDT >"2022-07-19 16:10" & MDT < "2022-07-19 16:37")

waterConcentration_plt(manualHeavy)
d180_time_plt(manualHeavy)

stds_071922 <- data_071922 %>% 
  filter(H2O_Batch == 0 | H2O_Batch == 106 | H2O_Batch == 247) %>% 
    flask_first3minutes() %>% 
     mutate(
       std = c("Ygrette4", "Ygrette4", "H072022"),
       T = 22,
       Analyst = "Haley",
       d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O_out,
       d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H_out
     ) 
```

## July 20, 2022 

```{r}
data_072022 <- tbl %>% 
  filter (DATE == "2022-07-20") %>% 
    BoulderTime() %>% 
      filter (MDT > "2022-07-20 12:45:00" & MDT < "2022-07-20 15:15") %>% 
        h2o_batches()

waterConcentration_plt(data_072022)
h2o_batch_plt(data_072022)
h2O_FirstThreeMinutes(data_072022 %>% filter (H2O_Batch>1))
d180_time_plt(data_072022)

stds_072022 <- data_072022 %>% 
  filter (H2O_Batch>1) %>% 
  flask_first3minutes() %>% 
  mutate(
    std = c("H072022", "H072022", "2019DI_Gallon", "2019DI_Gallon"),
       T = 22,
       Analyst = "Haley",
       d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O_out,
       d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H_out
  )
```


```{r}
julystd <- bind_rows(stds_071922, stds_072022) %>% 
  left_join(stds, by = "std")

d18O_lm_0722 <- lm(d18O_rothfuss ~ d18o_known, julystd) 
d2H_lm_0722 <- lm (d2H_rothfuss ~ d2H_known, julystd)

julystd <- julystd %>% 
  mutate(
    d18O_vsmow = (d18O_rothfuss - 0.7289) / 1.02,
    d2H_vsmow = (d2H_rothfuss - -.4987) / 1.0236
  )

julystd_plt <- julystd %>% 
  ggplot()+
  aes(x = d18O_vsmow, y = d2H_vsmow, color= std)+
  geom_errorbar(aes(ymin = d2H_vsmow - 2, ymax = d2H_vsmow + 2))+
  geom_errorbarh(aes(xmin = d18O_vsmow - 0.5, xmax = d18O_vsmow + 0.5))+
  geom_point() +
  geom_point(data = julystd, aes
             (x = d18o_known, y = d2H_known), color = "black")

ggplotly(julystd_plt)
```

## equations:
d18O_vsmow = (d18O_rothfuss - 0.7289) / 1.02,
d2H_vsmow = (d2H_rothfuss - -.4987) / 1.0236





# August 2022
Between August 5 - 12 we measured two SWISS pulled from the field, and so we also tried to measure our own standards in the meantime. Additionally, I tried to do a 'valco' run using the vaporizer system, but that run was unsuccessful. For these, we have some new standards:
* Benson DI 080222 -> BDI_080222
* Heavy #2 080322 -> H2_080322
* Light 8/3/22 #1 -> L1_080322 

## August 5, 2022

July 2, 2023 - 
Notes on code changes:
- Changed the time zone on the cut data to match notes. If running this in Colorado, re-update times.  
- Re-examined the calibration applied on the August 2022 data. Rather than keeping them separate, I combined all of the standards run between August 5 - August 12 as a pooled group. I did this in part because I primarily just ran DI water, and there was no discernible drift (within the uncertainty of the probes) . 


```{r}
data_080522 <- tbl %>% 
  filter(DATE == "2022-08-05") %>% 
    BoulderTime() %>% 
      filter (MDT > "2022-08-05 13:42" & MDT < "2022-08-05 14:30") %>% 
        h2o_batches()

waterConcentration_plt(data_080522)
h2o_batch_plt(data_080522)
h2O_FirstThreeMinutes(data_080522)

d2h <- data_080522 %>% 
  ggplot()+
  aes(x = MDT, y = Delta_D_H)+
  geom_point()

d2h

data_080522 %>% 
  filter(MDT > "2022-08-05 13:45" & MDT < "2022-08-05 13:57")%>% 
  ggplot()+
  aes(x = MDT, y = Delta_D_H)+
  geom_point()


stds_080522 <- data_080522 %>% 
  filter (H2O_Batch != 54) %>% 
  flask_first3minutes() %>% 
  mutate(
    std = c("BDI_080222", "Ygrette4"),
       T = 22,
       Analyst = "Haley"
  )
```
These averages are the same for d18O, but about 0.5 per mil lighter than haley's average. Definite downward trend in d2H value, so window matters. I would choose 14:50 - 14:55 



## August 9, 2022 probe stds
12:30 - 4:00
2 x ygrette4
  The first ygrette has a definite trend. Going to do that one by hand 

3 x BDI0800322
2 x Heavy2_080322

```{r}
data_080922 <- tbl %>% 
  filter (DATE == "2022-08-09") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-08-09 11:00" & MDT < "2022-08-09 15:00") %>% 
  h2o_batches()

ygrette <- data_080922 %>% 
  filter (MDT >"2022-08-09 11:45" & MDT < "2022-08-09 11:50") %>% 
  flask_out_ave() %>% 
  mutate(
     std = c("Ygrette4"),
     T = 22,
     Analyst = "Haley"
  )


h2o_batch_plt(data_080922 %>% filter(MDT > "2022-08-09 12:25:30"))
# the first plataeu is Ygrette4 #2, then three DIs and 2 Heavy's 

d180_time_plt(data_080922 %>% filter(MDT > "2022-08-09 12:25:30"))
h2O_FirstThreeMinutes(data_080922 %>% filter(H2O_Batch >179 & H2O > 15000))

stds_080922 <- data_080922 %>% 
  filter(H2O_Batch >179 & H2O > 15000) %>% 
  flask_first3minutes() %>% 
  mutate(
     std = c("Ygrette4", "BDI_080222", "BDI_080222", "BDI_080222", "H2_080322", "H2_080322"),
     T = 22,
     Analyst = "Haley"
  ) %>% 
  bind_rows(ygrette)
```

## Oglala Stds
```{r}
# oglalastds <- bind_rows(stds_080522, stds_080922) %>% 
#   left_join(stds, by = "std") %>% 
#   mutate(
#     d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O_out,
#     d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H_out
#   )
# 
# d18O_lm_080522 <- lm(d18O_rothfuss ~ d18o_known, oglalastds) 
# d2H_lm_080522 <- lm (d2H_rothfuss ~ d2H_known, oglalastds)
# 
# oglalastds <- oglalastds %>% 
#   mutate(
#     d18O_vsmow = (d18O_rothfuss - 0.711) / 1.018,
#     d2H_vsmow = (d2H_rothfuss - -0.4566) / 1.0297
#   )
# 
# oglalastd_plt <- oglalastds %>% 
#   ggplot()+
#   aes(x = d18O_vsmow, y = d2H_vsmow, color= std)+
#   geom_errorbar(aes(ymin = d2H_vsmow - 2, ymax = d2H_vsmow + 2))+
#   geom_errorbarh(aes(xmin = d18O_vsmow - 0.5, xmax = d18O_vsmow + 0.5))+
#   geom_point() +
#   geom_point(data = oglalastds, aes
#              (x = d18o_known, y = d2H_known), color = "black")
# 
# ggplotly(oglalastd_plt)

```
Equations:
d18O_vsmow = (d18O_rothfuss - 0.711) / 1.018,
d2H_vsmow = (d2H_rothfuss - -0.4566) / 1.0297  



## August 9 2022 vaporizer 
- Phlox 
- Started at approx. 17:54:00 

- well this calibration didn't work. The python code seems to have gotten stuck, and it didn't swap away from port 2 on the valco. 
```{r}
data_080922 <- tbl %>% 
  filter(DATE == "2022-08-09" | DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-08-09 16:45:00" & MDT < "2022-08-09 19:00:00")

waterConcentration_plt(data_080922)
d180_time_plt(data_080922)
```

## August 10 

Standard Name: Ygrette #4 (Light)
Sampled Time Frame: 11:04-11:07

Standard Name: Benson DI Aug 2, 2022
Sampled Time Frame: 11:51-11:54

Standard Name: Benson DI Aug 2, 2022
Approx. Start and End Time: 15:45-16:14

Standard Name: Benson DI Aug 2, 2022
Approx. Start and End Time: 16:17-16:25


```{r}
firstround_081022 <- tbl %>% 
  filter (DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-10 9:55" & MDT < "2022-08-10 11:00") %>% 
  h2o_batches()

h2o_batch_plt(firstround_081022)
d180_time_plt(firstround_081022)
d2H_time_plt(firstround_081022)
h2O_FirstThreeMinutes(firstround_081022)

stds_081022 <- firstround_081022 %>% 
  filter(H2O > 5000) %>% 
  flask_first3minutes() %>% 
  mutate(
    std = c("Ygrette4", "BDI_080222"),
     T = 27,
     Analyst = "Haley"
  )

secondbatch <-  tbl %>% 
  filter (DATE == "2022-08-10") %>% 
  BoulderTime() %>% 
    filter(MDT > "2022-08-10 15:00" & MDT < "2022-08-10 15:26") %>% 
      h2o_batches() 


secondbatch %>% h2o_batch_plt()
secondbatch %>% d180_time_plt()
secondbatch %>% h2O_FirstThreeMinutes()


DI_0822 <- secondbatch %>% 
        flask_first3minutes() %>% 
        mutate(
          std = c("BDI_080222", "BDI_080222"),
          T = 23,
          Analyst = "Haley"
  )


stds_081022 <- stds_081022 %>% 
  bind_rows(DI_0822)
```


## August 11
Standard Name: Benson DI Aug 2, 2022
Approx. Start and End Time: 9:41-9:52
batch 68

Standard Name: Benson DI Aug 2, 2022
Approx. Start and End Time: 10:24-10:34
batch 134

Standard Name: Benson DI Aug 2, 2022 (same liquid that was measured before measuring the flasks)
Approx. Start and End Time: 14:28-14:41
batch 399
Not stable - remove 

Standard Name: Light 8/3/22 #1
Approx. Start and End Time: 14:56-15:06
batch 482

Standard Name: Heavy Aug 3, 2022 #2
Approx. Start and End Time: 15:19-15:29
batch 564


```{r}
data_081122 <- tbl %>% 
  filter (DATE == "2022-08-11") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-11 8:30") %>% 
        h2o_batches() %>% 
          filter(H2O_Batch == 68 | H2O_Batch == 134 | H2O_Batch == 399 | H2O_Batch == 482 | H2O_Batch == 564)

h2o_batch_plt(data_081122)
d180_time_plt(data_081122)

stds_081122 <- data_081122 %>% 
  flask_first3minutes() %>% 
    mutate(
      std = c("BDI_080222", "BDI_080222", "BDI_080222", "L1_080322", "H2_080322"),
          T = 23,
          Analyst = "Haley"
    )
```




## August 12 

Standard Name: Light 8/3/22 #1
Approx. Start and End Time: 10:28-10:38
batch 51

Standard Name: Benson DI Aug 2, 2022
Approx. Start and End Time: 11:00-11:10
Sampled Time Frame: 11:05-11:08
batch 126


Standard Name: Heavy Aug 3, 2022 #2
Approx. Start and End Time: 11:33-11:43
batch 206 


```{r}
data_081222 <- tbl %>% 
  filter(DATE == "2022-08-12") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-12 9:20" & MDT < "2022-08-12 14:15") %>% 
        h2o_batches() %>% 
          filter(H2O_Batch == 51 | H2O_Batch == 126 | H2O_Batch ==206 | H2O_Batch == 463  | H2O_Batch == 623)



batch545 <- tbl %>% 
  filter(DATE == "2022-08-12") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-12 13:39:00" & MDT < "2022-08-12 13:42:01") %>% flask_out_ave() %>% 
        mutate(
          std = c("BDI_080222"),
          T = 23,
          Analyst = "Haley")
        

stds_081222 <- data_081222 %>% 
  flask_first3minutes() %>% 
   mutate(
      std = c("L1_080322", "BDI_080222", "H2_080322", "L1_080322", "H2_080322"),
          T = 23,
          Analyst = "Haley") %>% 
            bind_rows(batch545)

stds_081222 <- stds_081222 %>% filter(H2O_Batch != 206)
```

# Correction for July Briggsdale data 
These flasks and standards were measured 08/10 - 08/12, we included 08/09 for posterity 
```{r}
all_0822 <- bind_rows(stds_080522, stds_080922, stds_081022, stds_081122, stds_081222) %>% 
  liq_rothfuss2013() %>% 
  left_join(stds, by = "std")



#d18O correction
d18O_lm_0822 <- lm(d18O_liq ~ d18o_known, all_0822 %>% filter(H2O_Batch !=397)) 

d18O_unknowns<- all_0822 %>% ggplot()+
  aes(x = d18o_known, y = d18O_liq) +
  geom_point() +
  #geom_smooth(method = lm)+
  geom_abline(slope = d18O_lm_0822$coefficients[2], intercept = d18O_lm_0822$coefficients[1])

d18O_unknowns

#d2H correction
dD_lm_0822 <- lm(d2H_liq ~ d2H_known, all_0822 %>% filter(H2O_Batch !=397))

d2H_unknowns <-  all_0822 %>% ggplot()+
  aes(x = d2H_known, y = d2H_liq) +
  geom_point() +
  #geom_smooth(method = lm)+
  geom_abline(slope = dD_lm_0822$coefficients[2], intercept = dD_lm_0822$coefficients[1])

d2H_unknowns


all_0822 <- all_0822 %>% 
  mutate(
    d18O_corr = round(( (d18O_liq - d18O_lm_0822$coefficients[1])/d18O_lm_0822$coefficients[2]),1),
    dD_corr = round(( (d2H_liq - dD_lm_0822$coefficients[1])/dD_lm_0822$coefficients[2]),1),
  )
```
## Equations transferred to 
d18O_corr = (d18O_liq - 0.3336484) / 1.0072042
d2H_corr = (d2H_liq - -7.408711) / 1.008137 


## August 16 
Valco calibration done on the humidity system. one hour seems to be a good amount of time, could maybe be even longer

This was a practice calibration of sorts - running with Valerie. The water in the vials was old (> 1 week), and you can see the values are fairly evaporated compared to those from 2 days later
```{r}
data_081622 <- tbl %>% 
  filter(DATE == "2022-08-16" | DATE == "2022-08-17") %>% 
  BoulderTime() %>% 
  filter(MDT<"2022-08-17 03:03") 

waterConcentration_plt(data_081622)
d180_time_plt(data_081622)

KFW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 17:51" & MDT < "2022-08-16 18:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KFW")

KAW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 18:51" & MDT < "2022-08-16 19:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KAW")

KGW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 19:51" & MDT < "2022-08-16 20:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KGW")

KBW_0816 <- data_081622 %>% 
  filter (MDT > "2022-08-16 20:51" & MDT < "2022-08-16 21:06") %>% 
  flask_out_ave() %>% 
  mutate(std = "KBW")

stds_0817 <- bind_rows(KFW_0816, KAW_0816, KGW_0816, KBW_0816)


all_0816 <- full_join(stds_0817, stds, by = "std")

all_0816 %>% ggplot()+
  aes(x = d18o_known, y = d18O_out, size = 2)+
  geom_point()+ 
  geom_smooth(method = "lm", se = FALSE, aes(size = 0.5))

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all_0816)
dD_lm <- lm(d2H_out ~ d2H_known, all_0816)

#double check it worked
all_0816 <- all_0816 %>% 
  mutate(
    d18O_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )

print(d18O_lm$coefficients[1])
print(d18O_lm$coefficients[2])

```

### Equations transfered into corrections script
d18O_corr = (d18O_out - 0.7917232) / 1.02183
d2H_corr = (d2H_out - 2.226) / 1.036

## August 18
```{r}
data_081822 <- tbl %>% 
  filter(DATE == "2022-08-18" | DATE == "2022-08-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-18 16:30" & MDT < "2022-08-19 06:10")


waterConcentration_plt(data_081822)
d180_time_plt(data_081822)

kfw_0818 <- data_081822 %>% 
  filter(MDT > "2022-08-18 16:40" & MDT < "2022-08-18 17:00") %>% 
    flask_out_ave() %>% 
  mutate(std = "KFW")


kfw_0818_2 <- data_081822 %>% 
  filter(MDT > "2022-08-18 22:50" & MDT < "2022-08-18 23:00") %>% 
    flask_out_ave()

KAW_0818 <- data_081822 %>% 
  filter(MDT > "2022-08-18 17:40" & MDT < "2022-08-18 18:00") %>% 
    flask_out_ave() %>% 
  mutate(std = "KAW")

KAW2 <- data_081822 %>% 
  filter(MDT > "2022-08-18 21:40" & MDT < "2022-08-18 22:00") %>% 
    flask_out_ave()

KGW_0818 <- data_081822 %>% 
  filter(MDT > "2022-08-18 18:40" & MDT < "2022-08-18 19:00") %>% 
    flask_out_ave() %>% 
  mutate(std = "KGW")

KBW_0818 <- data_081822 %>% 
  filter(MDT > "2022-08-18 19:40" & MDT < "2022-08-18 20:00") %>% 
    flask_out_ave() %>% 
  mutate(std = "KBW")


stds_0818 <- bind_rows(kfw_0818, KAW_0818, KGW_0818, KBW_0818)


all_0818 <- full_join(stds_0818, stds, by = "std")


```


### linear regression

KFW didn't perform well, and KAW is corrected better if KFW is excluded 

Strongly considered taking out KBW as well, but didn't want to overconstrain, and the corrections do prety okay with KBW still in.

My preference is to get KAW right becuase that is closest to the values I'm measuring. 
```{r}
all_0818 %>% filter(std != "KFW")%>% ggplot()+
  aes(x = d18o_known, y = d18O_out)+
  geom_point(size = 5)+ 
  geom_smooth(method = "lm", se = FALSE, size = 0.5)

all_0818 %>% ggplot()+
  aes(x = d2H_known, y = d2H_out)+
  geom_point(size = 5)+ 
  geom_smooth(method = "lm", se = FALSE, size = 0.5)

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all_0818  %>% filter(std != "KFW"))
dD_lm <- lm(d2H_out ~ d2H_known, all_0818 %>% filter(std != "KFW"))

all_0818 <- all_0818 %>% 
  mutate(
    d18O_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )

d18O_lm
dD_lm

```

### Equations transfered into corrections script
d18O_corr = (d18O_out - 0.7713) / 1.0321,
d2H_corr = (d2H_out - 0.3376) / 1.0344

### Probe measurements

could add:
08-18 6:30 - 6:40 am, ran DI @ 150/50 through port 1 
08-18 6:40-7:02 am ran DI @ 60//20 through port 1
 —--------
Swapped probes, and swapped in Raclette
7:12 am started running @ 60/20 through port 1 on Raclette
7:25 - 7:34 am ran DI at 150/50 


```{r}
probe0817 <- tbl %>% 
  filter(DATE == "2022-08-18" |DATE == "2022-08-17") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-17 13:40" & MDT < "2022-08-17 22:56")

d180_time_plt(probe0817)

start15050 <- probe15050<- probe0817 %>% 
  filter(MDT > "2022-08-17 14:20" & MDT < "2022-08-17 14:25") %>% 
  flask_out_ave() %>% 
  mutate(MFC = "150/50")

endLindt <- probe0817 %>% 
  filter(MDT > "2022-08-17 22:02" & MDT < "2022-08-17 22:07") %>% 
  flask_out_ave() %>% 
  mutate(MFC = "150/50")

endLindt6020 <- probe0817 %>% 
  filter(MDT > "2022-08-17 22:20" & MDT < "2022-08-17 22:30") %>% 
  flask_out_ave() %>% 
  mutate(MFC = "60/20")

probe6020_0817 <- probe0817 %>% 
  filter(MDT > "2022-08-17 22:45" & MDT < "2022-08-17 22:48") %>% 
  flask_out_ave() %>% 
  mutate(MFC = "60/20")

probe15050<- probe0817 %>% 
  filter(MDT > "2022-08-17 22:52:30" & MDT < "2022-08-17 22:55:30") %>% 
  flask_out_ave() %>% 
  mutate(MFC = "150/50")

BDI_0817 <- bind_rows(start15050,endLindt, endLindt6020, probe6020_0817,probe15050)
```


## August 31 
done at 23:17?
No idea what went wrong in the code, but it only did KFW and KGW 

Probe data (manual on picarro): 
60/20 started at 6:36 pm
-26.0 ± 0.2 
-195.4 ± 0.5
29440 ± 90

Started a calibration at approx. 7 pm 
-30.1 ± 0.23
-198.4 ± 0.57
30520 ± 40



```{r}
data_083122 <- tbl %>% 
  filter(DATE == "2022-09-01") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-31 19:25" & MDT < "2022-09-01 06:17")

waterConcentration_plt(data_083122)
d180_time_plt(data_083122)

KFW_0831 <- data_083122 %>% 
  filter(MDT > "2022-08-31 20:08" & MDT < "2022-08-31 20:18") %>% 
  flask_out_ave() %>% 
  mutate(std = "KFW")

KGW_0831 <- data_083122 %>% 
  filter(MDT > "2022-08-31 21:08" & MDT < "2022-08-31 21:18") %>% 
  flask_out_ave() %>% 
  mutate(std = "KGW")

all_0831 <- bind_rows(KFW_0831, KGW_0831) %>% 
  full_join(stds, by = "std")
  
#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all_0831)
dD_lm <- lm(d2H_out ~ d2H_known, all_0831)

all_0831 <- all_0831 %>% 
  mutate(
    d18O_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )

d18O_lm
dD_lm

```

d18O_corr = (d18O_out - 1.289) / 1.039,
d2H_corr = (d2H_out - 4.558) / 1.049
