---
title: "Untitled"
author: "Rachel"
date: "8/11/2022"
output: html_document
---
The purpose of this markdown is to provide a place to do the data reduction on the vapor calibrations. 


```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(dplyr)
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     as_tibble() %>%
#     dplyr::select(1, 2, 15, 17, 18, 19)
# 
# currentdate <- Sys.Date()
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Standard values
```{r}
stds <- tibble(
  std = c("KFW", "KBW", "KAW", "KGW"),
  d18o_known = c(-0.76, -14.15, -30.30, -38.02),
  d2H_known = c(-2.82,-111.65,-239.13, -298.37),
  type = "known"
)
```

# March 18, 2022 calibration
Julien 
```{r}
data_031822 <- tbl %>% 
  filter(DATE == "2022-03-18" | DATE == "2022-03-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-18 12:00:00" & MDT < "2022-03-19 02:15:00")

d180_time_plt(data_031822)
waterConcentration_plt(data_031822)

KFW_031822 <- data_031822 %>% 
  filter(MDT >"2022-03-18 16:10:00" & MDT < "2022-03-18 17:00:00") %>% 
  flask_out_ave() %>% mutate (std = "KFW")


KAW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 18:45:00" & MDT < "2022-03-18 19:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_031822 <- data_031822 %>% 
  filter(MDT > "2022-03-18 21:20:00" & MDT < "2022-03-18 21:50:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_031822 <- data_031822 %>% filter(MDT > "2022-03-18 23:55:00" & MDT < "2022-03-19 00:20:00") %>% flask_out_ave() %>% mutate(std = "KBW")


observed_stds <- bind_rows(KFW_031822, KAW_031822, KGW_031822, KBW_031822) %>% 
  mutate(
    type = "Observed"
  )

all <- full_join(observed_stds, stds, by = "std")

all %>% ggplot()+
  aes(x = d18o_known, y = d18O_out)+
  geom_point()+
   geom_line()

#linearly regress 
d18O_lm <- lm(d18O_out ~ d18o_known, all)
dD_lm <- lm(d2H_out ~ d2H_known, all)

#double check it worked
all <- all %>% 
  mutate(
    d18O_iso_disc_corr = (d18O_out-d18O_lm$coefficients[1]) / d18O_lm$coefficients[2],
    dD_iso_disc_corr = (d2H_out-dD_lm$coefficients[1]) / dD_lm$coefficients[2],
  )


print(d18O_lm$coefficients[1])
print(d18O_lm$coefficients[2])

write.csv(data_031822, "data_031822.csv")
```
## Equations transfered into corrections script
d18O_corr = (d18O_out - 1.68206) / 1.026412
d2H_corr = (d2H_out - 5.669731) / 1.045704


# April 3, 2022 Calibration 
Julien 
```{r}
data_040422 <- tbl %>% 
  filter(DATE == "2022-04-04" | DATE == "2022-04-05") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

#waterConcentration_plt(data_040422)

KFW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422 <- data_040422 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422 <- data_040422 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422 <- bind_rows(KFW_040422, KAW_040422, KGW_040422, KBW_040422) %>% 
  full_join(stds, by = "std")

stds_plt <- stds_040422 %>% 
  ggplot()+
    aes(x = d18o_known, y = d18O_out)+
    geom_point()+
    geom_line()

d18O_lm_0404 <- lm(d18O_out ~ d18o_known, stds_040422)
dD_lm_0404 <- lm(d2H_out ~ d2H_known, stds_040422)

stds_040422 <- stds_040422 %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404$coefficients[1])/d18O_lm_0404$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404$coefficients[1])/dD_lm_0404$coefficients[2],
  )
```

## Equations copied into corrections script
d18O_corr = (d18O_out - 1.4572)/1.0281
d2H_corr = (d2H_out - 5.595052)/1.046536


#April 4 on Phlox
```{r}
phlox0404 <- 
    list.files ("data/Phlox_April4", pattern = "*.dat", recursive = T, full.names = T) %>%
    map_df(~read_table2(.)) %>%
    as_tibble() %>%
    dplyr::select(1, 2, 15, 17, 18, 19)

phlox0404 <- phlox0404 %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 15:00:00" & MDT < "2022-04-05 01:00:00")

waterConcentration_plt(phlox0404)

KFW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 15:30:00" & MDT < "2022-04-04 16:15:00") %>% 
  flask_out_ave() %>% mutate(std = "KFW")

KAW_040422_phlox <- phlox0404 %>% 
  filter(MDT> "2022-04-04 18:00:00" & MDT < "2022-04-04 18:30:00") %>% 
  flask_out_ave() %>% mutate(std = "KAW")

KGW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 20:40:00" & MDT < "2022-04-04 21:10:00") %>% 
  flask_out_ave() %>% mutate(std = "KGW")

KBW_040422_phlox <- phlox0404 %>% 
  filter(MDT > "2022-04-04 23:10:00" & MDT < "2022-04-04 23:40:00") %>% 
  flask_out_ave() %>% mutate(std = "KBW")

stds_040422_phlox <- bind_rows(KFW_040422_phlox, KAW_040422_phlox, KGW_040422_phlox, KBW_040422_phlox) %>% 
  full_join(stds, by = "std")


d18O_lm_0404_phlox <- lm(d18O_out ~ d18o_known, stds_040422_phlox)
dD_lm_0404_phlox <- lm(d2H_out ~ d2H_known, stds_040422_phlox)


stds_040422_phlox <- stds_040422_phlox %>% 
  mutate(
    d18O_disc_corr = ((d18O_out-d18O_lm_0404_phlox$coefficients[1])/d18O_lm_0404_phlox$coefficients[2]),
    dD_disc_corr = (d2H_out-dD_lm_0404_phlox$coefficients[1])/dD_lm_0404_phlox$coefficients[2],
  )

stds_040422_phlox <- stds_040422_phlox %>% April4_phlox_corr()

```

d18O_corr_phlox = (d18O_out - 4.229)/1.045868
d2H_corr_phlox = (d2H_out + 0.00710443)/1.050112



















# August 9 
Phlox 
