---
title: "Fondue QAQC"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---
# Setup & Load Data
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
## load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```


```{r load data}
tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Dry Air Test - 
Air out of flasks on 03-01-2021
```{r Fondue Dry Air 1}
data030121 <- tbl %>% filter (DATE == "2021-03-01") %>% 
  mutate(
    UTC = hms(TIME),
    UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
    MDT = with_tz(UTC_full, tzone = "America/Denver"),
    seconds = row_number()
         ) %>% #uses the lubridate to replicate the time, but makes it filterable 
  filter (UTC > "20H 10M 00S" & UTC < "21H 30M 00S")  

dryair_concentration <- data030121 %>% 
  ggplot()+
  aes(TIME, H2O) +
  geom_point()

ggplotly(dryair_concentration, dynamicTicks = TRUE)

dryair_results <- data030121 %>% 
  filter(UTC > "20H 13M 20S" & UTC < "20H 15M 00S") %>% 
    summarise(
      Flask = 2,
      SD = sd(H2O),
      H2O = mean(H2O)
    )

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 17M 40S" & UTC < "20H 20M 00S") %>% 
    summarise(
      Flask = 3,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 23M 20S" & UTC < "20H 25M 00S") %>% 
    summarise(
      Flask = 4,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 29M 00S" & UTC < "20H 30M 40S") %>% 
    summarise(
      Flask = 5,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 35M 40S" & UTC < "20H 37M 00S") %>% 
    summarise(
      Flask = 6,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 41M 00S" & UTC < "20H 42M 40S") %>% 
    summarise(
      Flask = 7,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 46M 20S" & UTC < "20H 48M 00S") %>% 
    summarise(
      Flask = 8,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 52M 00S" & UTC < "20H 53M 40S") %>% 
    summarise(
      Flask = 9,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 56M 20S" & UTC < "20H 58M 00S") %>% 
    summarise(
      Flask = 10,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "21H 03M 00S" & UTC < "21H 04M 40S") %>% 
    summarise(
      Flask = 11,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 10M 20S" & UTC < "21H 12M 00S") %>% 
    summarise(
      Flask = 12,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 15M 20S" & UTC < "21H 17M 00S") %>% 
    summarise(
      Flask = 13,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 20M 20S" & UTC < "21H 22M 00S") %>% 
    summarise(
      Flask = 15,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 26M 20S" & UTC < "21H 28M 00S") %>% 
    summarise(
      Flask = 16,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results  %>% mutate (Color = ifelse(H2O > 250, "red", "black"))

dryair_plot <- dryair_results %>% ggplot()+
  aes(Flask, H2O, color = Color, size = 3)+
  geom_point() +
  scale_color_identity()

dryair_plot
```

In response to these results:
*port 3 - tightened valco side both top and bottom, tightened glass side on 3T (1/2 - 3/4 turn)
*port 7 - tightened valco side both top and bottom, tightened glass side on 7B, SS side on 7B
*port 8 - nothing (missed it)
*port 11 - tightened valco side both top and bottom, 1/8th turn on 11T glass, 1/8th turn on 11B glass

# Water Vapor Test 
## Water Vapor In 
March 7, 2021 

```{r 030721 water vapor in}
data_030721 <- tbl %>% 
  filter(DATE == "2021-03-07" | DATE == "2021-03-08") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>% 
      filter(MDT > "2021-03-07 9:45:00" & MDT < "2021-03-07 20:25:00")

vaporin_concentration <- data_030721 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

print(vaporin_concentration)

  playplot <- data_030721 %>%
    filter(MDT > "2021-03-07 14:00:00" & MDT < "2021-03-07 16:00:00") %>%
    ggplot()+
    aes(UTC, H2O) +
    geom_point()

  ggplotly(playplot, dynamicTicks = TRUE)

  d18Oplayplot <- data_030721 %>%
   filter(MDT > "2021-03-07 14:00:00" & MDT < "2021-03-07 16:00:00") %>%
    ggplot()+
    aes(UTC, Delta_18_16) +
    geom_point()

  ggplotly(d18Oplayplot, dynamicTicks = TRUE)

fondue_vaporin <- data_030721 %>% 
   filter(MDT > "2021-03-07 13:33:00" & MDT < "2021-03-07 13:40:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 2)





fondue_vaporin <- fondue_vaporin %>% 
  bind_rows(
    data_030721 %>% 
      filter(MDT > "2021-03-07 13:47:00" & MDT < "2021-03-07 13:57:00") %>%
      flask_out_ave() %>% 
        mutate(Flask =3)
  )
    

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 14:34:00" & MDT < "2021-03-07 14:44:00") %>%
    flask_out_ave() %>% 
      mutate(Flask =4)
)


fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 15:11:00" & MDT < "2021-03-07 15:21:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 5)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 15:11:00" & MDT < "2021-03-07 15:21:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 6)
)

fondue_vaporin <- fondue_vaporin %>% 
  bind_rows(
    data_030721 %>% 
      filter(MDT > "2021-03-07 15:37:00" & MDT < "2021-03-07 15:47:00") %>%
        flask_out_ave() %>% 
          mutate(Flask = 7)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 16:40:00" & MDT < "2021-03-07 16:47:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 8)
)

fondue_vaporin <- fondue_vaporin %>%  bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 16:55:00" & MDT < "2021-03-07 17:05:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 9)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 17:13:00" & MDT < "2021-03-07 17:23:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 10)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
    filter(MDT > "2021-03-07 17:31:30" & MDT < "2021-03-07 17:41:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 11)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 17:49:30" & MDT < "2021-03-07 17:59:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 12)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:07:00" & MDT < "2021-03-07 18:17:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 13)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:35:00" & MDT < "2021-03-07 18:45:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 14)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:52:30" & MDT < "2021-03-07 19:02:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 15)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 19:12:30" & MDT < "2021-03-07 19:22:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 16)
)

fondue_vaporin <- fondue_vaporin %>% 
  mutate(
    date = 030721,
    datatype = "VaporIn"
  )

```

## Water Vapor Out
March 21, 2021
```{r 032121 water vapor out}
data032121 <- tbl %>%
  filter (DATE == "2021-03-21") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>%
      filter (MDT > "2021-03-21 10:39:00"  & MDT < "2021-03-21 11:54:15") 

vaporout_concentration <- data032121 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

ggplotly(vaporout_concentration, dynamicTicks = TRUE)

outlet_032121 <- outlet_batches(data032121)
outlet_plt_032121 <- outlet_batch_plt(outlet_032121)

flask_ave_032121 <- flask_ave_outlet(outlet_032121) %>% 
  mutate(
    Flask = c(2, 3, 4, 5, 6, 7,8,9,10,11,12,13,14,15,16)
  )

```

These data were hand averaged while taking the data. That data can be found on Rachel's laptop in PhD 2020 -2021/Fall_2020_SWISS_tests. I compared the 'autoreduced' data with the hand averaged data. They were quite close (within SD) fpr h20 concentration and d18O. For d2H they were usually close except for the flasks that had a really high SD(2+ per mil).

## Compare in and out 
```{r h2o hold test results}
fondue_comparison <- left_join(fondue_vaporin, flask_ave_032121, by = "Flask") %>% 
  mutate(
    H2O_diff = H2O_out.y- H2O_out.x,
    d18O_diff = d18O_out.y - d18O_out.x,
    d2H_diff = d2H_out.y - d2H_out.x
  )

compare_plot <- fondue_comparison %>% select(Flask, H2O_diff, d18O_diff, d2H_diff) %>% 
  pivot_longer(cols = c(H2O_diff, d18O_diff, d2H_diff))  %>%   
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode("$\\Delta H_2O$" = "H2O_diff",
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(Flask, value)+
        geom_point()+
        scale_color_discrete(labels = latex_labeller) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()
           
print(compare_plot)

compareplt2 <- fondue_comparison %>% select(Flask, H2O_diff, d18O_diff, d2H_diff) %>% 
  pivot_longer(cols = c(H2O_diff, d18O_diff, d2H_diff))  %>%   
  filter(Flask != 6 & Flask != 7) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode("$\\Delta H_2O$" = "H2O_diff",
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(Flask, value)+
        geom_point()+
        scale_color_discrete(labels = latex_labeller) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()

print(compareplt2)
```

Based on these plots: 
  1. I am confused about flasks 6 --> surprised its so bad. but moves towards room quite a bit. 7 is essentially just room. 
  1. I think flasks 3 and 8 are still leaking -> this makes sense because I didn't do anything with 8 and 3 turned a lot
  1. I think I should try and heat the flasks because the hydrogen isotopes are so weird

# 40 day dry air 
```{r 072021}
data_072021 <- tbl %>%
  filter (DATE == "2021-07-20") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>%
      filter (MDT < "2021-07-20 16:58:15")

outlet_072021 <- outlet_batches(data_072021)
outlet_plt_072021 <- outlet_batch_plt(
  outlet_072021 %>% 
    filter(newbatch != 0 & newbatch != 7 & newbatch != 19 & newbatch != 26 & newbatch !=33 & newbatch != 38 & newbatch != 44)
  ) 
  
ggplotly(outlet_plt_072021, dynamicTicks = TRUE)

flask_ave_072021 <-  flask_ave_outlet(outlet_072021) %>% 
  filter(batch != 0 & batch != 7 & batch != 19 & batch != 26 & batch !=33 & batch != 38 & batch != 44) %>% 
  mutate(Flask = c(16, 15, 14, 13, 12, 11, 10))
```

```{r 072121}
data_072121 <- tbl %>%
  filter (DATE == "2021-07-21") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>% 
  filter (MDT > "2021-07-21 09:06:54" & MDT < "2021-07-21 12:06:28")

outlet_072121 <- outlet_batches(data_072121)
outlet_plt_072121 <- outlet_batch_plt(outlet_072121)
ggplotly(outlet_plt_072121)

flask_ave_072121 <-  flask_ave_outlet(
  outlet_072121 %>% 
    filter(batch!=0 & batch!=8 & batch!=16 & batch !=25 & batch!=33 & batch !=41 & batch!=48 & batch !=57 )) %>% 
  mutate(Flask = c(9,8,7,6,5,4,3,2))
```

```{r 40 day dry air}
dryair_40day <- bind_rows(flask_ave_072021, flask_ave_072121) %>% 
  Flask_h2o_plt()
```

# 7 Day Dry Air 
```{r 072821}
data_072821 <- tbl %>%
  filter (DATE == "2021-07-28") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>%
      filter (MDT > "2021-07-28 10:50:42"  & MDT < "2021-07-28 12:07:10") 

vaporout_concentration <- data_072821 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

ggplotly(vaporout_concentration, dynamicTicks = TRUE)

outlet_072821 <- outlet_batches(data_072821)
outlet_plt_072821 <- outlet_batch_plt(outlet_072821)

flask_ave_072821 <- flask_ave_outlet(outlet_072821) %>% 
  mutate(
    Flask = c(2, 3, 4, 5, 6, 7,8,9,10,11,12,13,14,15,16)
  )

flask_ave_072821_plt <- Flask_h2o_plt(flask_ave_072821)

```

```{r 090821}
data_090821 <- tbl %>% 
  filter(DATE == "2021-09-08") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>% 
        filter (MDT > "2021-09-08 09:00:00" & MDT < "2021-09-08 11:21:33") %>% 
          outlet_batches()

vaporout_concentration <- data_090821 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

ggplotly(vaporout_concentration, dynamicTicks = TRUE)

outlet_plt_090821 <-outlet_batch_plt(data_090821)
ggplotly(outlet_plt_090821, dynamicTicks = TRUE)

#flask 3 is gonna be a problem 
flask3_090821 <- data_090821 %>% 
  filter (MDT > "2021-09-08 11:10:35" & MDT < "2021-09-08 11:13:35") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 3)

flask_ave_090821 <- data_090821 %>% 
  filter(batch != 0 & batch !=7 & batch!=16 & batch!=24 & batch !=32) %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = c(16,15,14,13,12,11,10,9,8,7,6,5,4,2))  %>% 
  bind_rows(flask3_090821)

plt_flasks_090821 <- flask_ave_090821 %>% Flask_h2o_plt()
```

#43 day dry air test
Deployed at Briggsdale, including nights w/ freezing temps
```{r 102821}
data_102821 <- tbl %>% 
  filter(DATE == "2021-10-28") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>% 
        filter (MDT > "2021-10-28 14:23:28" & MDT < "2021-10-28 16:00:30") %>% 
          outlet_batches()

vaporout_concentration <- data_102821 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

ggplotly(vaporout_concentration, dynamicTicks = TRUE)

outlet_plt_102821 <-data_102821 %>% 
  filter(newbatch != 16 & newbatch!=8) %>% 
  outlet_batch_plt()

ggplotly(outlet_plt_102821, dynamicTicks = TRUE)

flask12_102821 <- data_102821 %>% 
  filter(MDT > "2021-10-28 15:51:00" & MDT < "2021-10-28 15:54:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 12)

flask_ave_102821 <- data_102821 %>% 
  filter(batch != 16 & batch!=8  & batch !=33) %>% 
    flask_ave_outlet() %>% 
      mutate(Flask = c(2,3,4,5,6,7,8,9,10,11,13)) %>% 
        bind_rows(flask12_102821)

plt_flasks_102821 <- flask_ave_102821 %>% 
  ggplot()+
  aes(x = Flask, y = H2O_out, size = 2)+
  geom_point(color = "black") +
  scale_y_continuous(limits =c(0, 3000), expand = c(0,0)) +
  scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
  theme_figure() +
  labs(
    y = latex2exp::TeX("$H_2O (ppm)$"),
    title = "Fondue",
    subtitle = "43 Days"
  ) +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5) ,
    plot.subtitle = element_text(hjust = 0.5)
  )

plt_flasks_102821
```


# Second Water vapor test
## March 19
The fill data is split between two days - march 19 and march 20. For march 19, I had to do a more manual "water batches" to lower the threshold so that flasks got differentiated.

also, last three minutes didn't work - needed to be cut off by 15 fewer seconds
```{r}
data_0301922 <- tbl %>% 
  filter(DATE == "2022-03-19" | DATE == "2022-03-20") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-19 19:05:00" & MDT < "2022-03-19 21:50:00") %>% 
  mutate(
    seconds = row_number(),
    waterdiff = H2O-70 > as.numeric(c("", head(H2O, -1))),
    waterdiff = ifelse (is.na(waterdiff), F, waterdiff),
    H2O_Batch = cumsum(waterdiff),
    H2O_Newbatch = as.character(H2O_Batch)
  )

waterConcentration_plt(data_0301922)
h2o_batch_plt(data_0301922)

h2o_LastThreeMinutes(data_0301922)

flasks_031922 <- data_0301922 %>% 
  group_by(H2O_Batch) %>% 
      mutate( 
        row = row_number(),
        totalrows= n()
      ) %>% 
        filter (totalrows > 100 & row < (totalrows - 80) & row > (totalrows - 320)) %>% 
              flask_out_ave() %>% 
            mutate(Flask = c(1:10))

```

##  March 20 
```{r}
data_032022 <- tbl %>% 
  filter(DATE == "2022-03-20") %>% 
  BoulderTime() %>% 
  filter( MDT > "2022-03-20 07:37:00" & MDT < "2022-03-20 09:30:00") %>% 
  h2o_batches()

waterConcentration_plt(data_032022)
h2o_batch_plt(data_032022)

h2o_LastThreeMinutes(data_032022)

flasks_032022 <- data_032022 %>% 
  group_by(H2O_Batch) %>% 
      mutate( 
        row = row_number(),
        totalrows= n()
      ) %>% 
        filter (totalrows > 100 & row < (totalrows - 100) & row > (totalrows - 340)) %>% 
              flask_out_ave() %>% 
            mutate(Flask = c(1, 11:16))

fondue_flasks_march2022 <- bind_rows(flasks_031922, flasks_032022)

fondue_flasks_march2022 <- fondue_flasks_march2022 %>% march182022_corr()
```

## April 3, 2022

Note: I wasn't getting good data prior to flask 11 - I paused and changed out the ptfe ferrule for a stainless steel one. 
I am concerned by flask 2. I used batch 829 for Flask 2. One way you can really see the difference is that there are dry air batches after I switcehd the ferrule
```{r}
data_040322 <- tbl %>% 
  filter(DATE == "2022-04-03") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-03 08:42:00" & MDT < "2022-04-03 13:30:00") %>% 
  h2o_batches()

waterConcentration_plt(data_040322)
d180_time_plt(data_040322)

h2o_batch_plt(data_040322)

data_040322 %>% 
  filter(H2O > 5000) %>% 
  h2O_FirstThreeMinutes()

flasks_040322 <- data_040322 %>% 
  filter(H2O > 5000) %>% 
  #filter(H2O_Batch != 734) %>% 
  flask_first3minutes() %>% 
  mutate(Flask = c(16:2,2)) %>% 
  April42022_corr()
```

## Difference
```{r}

WVtest_results <- fondue_flasks_march2022 %>% 
  left_join(flasks_040322, by = "Flask") %>% 
    mutate(
      d18O_diff = d18O_corr.y - d18O_corr.x,
      d2H_diff =   d2H_corr.y - d2H_corr.x
    )

WVtest_results_plt <- WVtest_results %>% 
  filter(Flask > 2) %>% 
  pivot_longer(cols = c(d18O_diff, d2H_diff)) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode(
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(x = Flask, y = value, size = 2) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        geom_point()+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()+
        theme(
          legend.position = "none"
        )

print(WVtest_results_plt)

```







