---
title: "Fondue QAQC"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---

```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
## load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

# source all relevant scripting files
source(file.path("scripts", "plotting_functions.R"))
source(file.path("scripts", "flask_ave.R"))
source(file.path ("scripts", "Eriks_functions.R"))
source(file.path ("scripts", "outlet_cut_functions.R"))
source(file.path ("scripts", "flask_plts.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```


# Load Data - 
This only needs to be run when there is new data, otherwise it will be much faster to load the RDS file in the last, commented line. 
```{r load data}
# tbl <-
#     list.files ("data_raw", pattern = "*.dat", recursive = T, full.names = T) %>% 
#     map_df(~read_table2(.)) %>% 
#     select(1, 2, 17, 18, 19)
# 
# currentdate <- Sys.Date()
# saveRDS(tbl, paste("data_raw/FondueData", currentdate,".RDS"))

tbl <- readRDS(file.path("data", "2021Data.RDS")) 
```

# Dry Air Test - 
Air out of flasks on 03-01-2021
```{r Fondue Dry Air 1}
data030121 <- tbl %>% filter (DATE == "2021-03-01") %>% 
  mutate(
    UTC = hms(TIME),
    UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
    MDT = with_tz(UTC_full, tzone = "America/Denver"),
    seconds = row_number()
         ) %>% #uses the lubridate to replicate the time, but makes it filterable 
  filter (UTC > "20H 10M 00S" & UTC < "21H 30M 00S")  

dryair_concentration <- data030121 %>% 
  ggplot()+
  aes(TIME, H2O) +
  geom_point()

ggplotly(dryair_concentration, dynamicTicks = TRUE)

dryair_results <- data030121 %>% 
  filter(UTC > "20H 13M 20S" & UTC < "20H 15M 00S") %>% 
    summarise(
      Flask = 2,
      SD = sd(H2O),
      H2O = mean(H2O)
    )

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 17M 40S" & UTC < "20H 20M 00S") %>% 
    summarise(
      Flask = 3,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 23M 20S" & UTC < "20H 25M 00S") %>% 
    summarise(
      Flask = 4,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 29M 00S" & UTC < "20H 30M 40S") %>% 
    summarise(
      Flask = 5,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 35M 40S" & UTC < "20H 37M 00S") %>% 
    summarise(
      Flask = 6,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 41M 00S" & UTC < "20H 42M 40S") %>% 
    summarise(
      Flask = 7,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 46M 20S" & UTC < "20H 48M 00S") %>% 
    summarise(
      Flask = 8,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 52M 00S" & UTC < "20H 53M 40S") %>% 
    summarise(
      Flask = 9,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "20H 56M 20S" & UTC < "20H 58M 00S") %>% 
    summarise(
      Flask = 10,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
  filter(UTC > "21H 03M 00S" & UTC < "21H 04M 40S") %>% 
    summarise(
      Flask = 11,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 10M 20S" & UTC < "21H 12M 00S") %>% 
    summarise(
      Flask = 12,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 15M 20S" & UTC < "21H 17M 00S") %>% 
    summarise(
      Flask = 13,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 20M 20S" & UTC < "21H 22M 00S") %>% 
    summarise(
      Flask = 15,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results %>% bind_rows(
  data030121 %>% 
   filter(UTC > "21H 26M 20S" & UTC < "21H 28M 00S") %>% 
    summarise(
      Flask = 16,
      SD = sd(H2O),
      H2O = mean(H2O)
    )
)

dryair_results <- dryair_results  %>% mutate (Color = ifelse(H2O > 250, "red", "black"))

dryair_plot <- dryair_results %>% ggplot()+
  aes(Flask, H2O, color = Color, size = 3)+
  geom_point() +
  scale_color_identity()

dryair_plot
```

In response to these results:
*port 3 - tightened valco side both top and bottom, tightened glass side on 3T (1/2 - 3/4 turn)
*port 7 - tightened valco side both top and bottom, tightened glass side on 7B, SS side on 7B
*port 8 - nothing (missed it)
*port 11 - tightened valco side both top and bottom, 1/8th turn on 11T glass, 1/8th turn on 11B glass

# Water Vapor Test 
## Water Vapor In 
March 7, 2021 

```{r}
data_030721 <- tbl %>% 
  filter(DATE == "2021-03-07" | DATE == "2021-03-08") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>% 
      filter(MDT > "2021-03-07 9:45:00" & MDT < "2021-03-07 20:25:00")

vaporin_concentration <- data_030721 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

print(vaporin_concentration)

  playplot <- data_030721 %>%
    filter(MDT > "2021-03-07 14:00:00" & MDT < "2021-03-07 16:00:00") %>%
    ggplot()+
    aes(UTC, H2O) +
    geom_point()

  ggplotly(playplot, dynamicTicks = TRUE)

  d18Oplayplot <- data_030721 %>%
   filter(MDT > "2021-03-07 14:00:00" & MDT < "2021-03-07 16:00:00") %>%
    ggplot()+
    aes(UTC, Delta_18_16) +
    geom_point()

  ggplotly(d18Oplayplot, dynamicTicks = TRUE)

fondue_vaporin <- data_030721 %>% 
   filter(MDT > "2021-03-07 13:33:00" & MDT < "2021-03-07 13:40:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 2)





fondue_vaporin <- fondue_vaporin %>% 
  bind_rows(
    data_030721 %>% 
      filter(MDT > "2021-03-07 13:47:00" & MDT < "2021-03-07 13:57:00") %>%
      flask_out_ave() %>% 
        mutate(Flask =3)
  )
    

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 14:34:00" & MDT < "2021-03-07 14:44:00") %>%
    flask_out_ave() %>% 
      mutate(Flask =4)
)


fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 15:11:00" & MDT < "2021-03-07 15:21:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 5)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 15:11:00" & MDT < "2021-03-07 15:21:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 6)
)

fondue_vaporin <- fondue_vaporin %>% 
  bind_rows(
    data_030721 %>% 
      filter(MDT > "2021-03-07 15:37:00" & MDT < "2021-03-07 15:47:00") %>%
        flask_out_ave() %>% 
          mutate(Flask = 7)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
   filter(MDT > "2021-03-07 16:40:00" & MDT < "2021-03-07 16:47:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 8)
)

fondue_vaporin <- fondue_vaporin %>%  bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 16:55:00" & MDT < "2021-03-07 17:05:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 9)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 17:13:00" & MDT < "2021-03-07 17:23:00") %>%
    flask_out_ave() %>% 
      mutate(Flask = 10)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
    filter(MDT > "2021-03-07 17:31:30" & MDT < "2021-03-07 17:41:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 11)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 17:49:30" & MDT < "2021-03-07 17:59:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 12)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:07:00" & MDT < "2021-03-07 18:17:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 13)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:35:00" & MDT < "2021-03-07 18:45:00") %>%
    flask_out_ave() %>% 
    mutate(Flask = 14)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 18:52:30" & MDT < "2021-03-07 19:02:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 15)
)

fondue_vaporin <- fondue_vaporin %>% bind_rows(
  data_030721 %>% 
  filter(MDT > "2021-03-07 19:12:30" & MDT < "2021-03-07 19:22:30") %>%
    flask_out_ave() %>% 
    mutate(Flask = 16)
)

fondue_vaporin <- fondue_vaporin %>% 
  mutate(
    date = 030721,
    datatype = "VaporIn"
  )

```

## Water Vapor Out
March 21, 2021
```{r}
data032121 <- tbl %>%
  filter (DATE == "2021-03-21") %>% 
    mutate(
      UTC = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"),
      MDT = with_tz(UTC, tzone = "US/Mountain"),
      seconds = row_number()
    ) %>%
      filter (MDT > "2021-03-21 10:39:00"  & MDT < "2021-03-21 11:54:15") 

vaporout_concentration <- data032121 %>% 
  ggplot()+
  aes(MDT, H2O) +
  geom_point()

ggplotly(vaporout_concentration, dynamicTicks = TRUE)

outlet_032121 <- outlet_batches(data032121)
outlet_plt_032121 <- plt_outlet_batch(outlet_032121)

flask_ave_032121 <- flask_ave_outlet(outlet_032121) %>% 
  mutate(
    Flask = c(2, 3, 4, 5, 6, 7,8,9,10,11,12,13,14,15,16)
  )



```

## Compare in and out 
```{r}
fondue_comparison <- left_join(fondue_vaporin, vaporout, by = "Flask") %>% 
  mutate(
    H2O_diff = H2O_out - H2O,
    d18O_diff = d180_out - d180,
    d2H_diff = d2H_out - d2H
  )

compare_plot <- fondue_comparison %>% select(Flask, H2O_diff, d18O_diff, d2H_diff) %>% 
  pivot_longer(cols = c(H2O_diff, d18O_diff, d2H_diff))  %>% 
      ggplot()+
        aes(Flask, value)+
        geom_point()+
        facet_wrap(~name, scales = "free")
           
ggplotly(compare_plot, dynamicTicks = TRUE)
```

Based on these plots: 
  1. I am confused about flasks 6 --> surprised its so bad. but moves towards room quite a bit. 7 is essentially just room. 
  1. I think flasks 3 and 8 are still leaking -> this makes sense because I didn't do anything with 8 and 3 turned a lot
  1. I think I should try and heat the flasks because the hydrogen isotopes are so weird



#Vapor Probe tests 
March 17 and 18, 2021 
