---
title: "QAQC of Lindt"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---

#Setup
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path ("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#Load 2021 data
tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Dry Air 1
```{r 061621}
data_061621 <- tbl %>% 
  filter(DATE == "2021-06-16") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-06-16 14:59:25" & MDT < "2021-06-16 16:15:00" )

#use these two plots to honein on the timing
waterConcentration_plt(data_061621)
outletValve_plt(data_061621)

#cut up the data
data_061621 <- data_061621 %>% 
  outlet_batches()

outlet_batch_plt(data_061621)

flask6_061621 <- data_061621 %>% 
  filter (MDT > "2021-06-16 15:22:24" & MDT < "2021-06-16 16:25:10" ) %>% 
    flask_out_ave() %>% 
      mutate(Flask = 6)

flask_ave_061621 <- data_061621 %>% 
  flask_ave_outlet() %>% 
    mutate(Flask = c(2,3,4,5,7,8,9,10,11,12,13,14,15,16)) %>% 
      bind_rows(flask6_061621)

flask_ave_061621_plt <- Flask_h2o_plt(flask_ave_061621)
```

# Dry Air 2
```{r 070421}
data_070421 <- tbl %>% 
  filter(DATE == "2021-07-04") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-07-04 12:01:52" & MDT < "2021-07-04 13:22:22")


waterConcentration_plt(data_070421)
outletValve_plt(data_070421)

flask12_070421 <- data_070421 %>% 
  filter(MDT > "2021-07-04 12:53:22" & MDT < "2021-07-04 12:56:22") %>% 
    flask_out_ave() %>% 
      mutate(Flask = 12)

flask2redo <- data_070421 %>% 
  filter(MDT > "2021-07-04 13:18:00" & MDT < "2021-07-04 13:20:00") %>% 
      flask_out_ave() %>% 
        mutate(Flask = 2.1)

flask4_070421 <- data_070421 %>%
  filter(MDT > "2021-07-04 12:13:22" & MDT < "2021-07-04 12:16:22") %>% 
    flask_out_ave() %>% 
      mutate(Flask = 4)

flask8_070421 <- data_070421 %>%
  filter(MDT > "2021-07-04 12:33:22" & MDT < "2021-07-04 12:36:22") %>% 
    flask_out_ave() %>% 
      mutate(Flask = 8)

data_070421 <- data_070421 %>% 
  outlet_batches()

outlet_batch_plt(data_070421)

flask_ave_070421 <- data_070421 %>% 
  filter(batch<41) %>% 
  flask_ave_outlet() %>% 
    mutate(Flask = c(2,3,5,6,7,9,10,11,13,14,15,16)) %>% 
      bind_rows(flask12_070421, flask2redo, flask4_070421, flask8_070421)

flask_ave_070421_plt <- Flask_h2o_plt(flask_ave_070421)
```


# Wate vapor 1
note: "unzipped", started measuring at flask 16 
Filled with Ygrette
```{r}
data_081121 <- tbl %>% 
  filter(DATE == "2021-08-11")  %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-08-11 10:14:07" & MDT < "2021-08-11 12:50:38")

waterConcentration_plt(data_081121)
outletValve_plt(data_081121)

data_081121 <- data_081121 %>% 
  outlet_batches()

outlet_batch_plt(data_081121)

flask_ave_081121 <- data_081121 %>% 
  flask_ave_outlet() %>% 
    filter(H2O_out > 500) %>% 
      filter (batch != 130) %>% 
        mutate(Flask = c(16, 15, 14, 13, 12, 11, 10, 9, 8, 7, 6,5,4,3,2))
  

plt_081121 <- flask_ave_081121 %>% 
  pivot_longer(cols = c(d18O_out, d2H_out)) %>% 
    ggplot()+
    aes(x = Flask, y = value, size = 2) +
    facet_wrap (~name, scales = "free", ncol = 1) +
    geom_point()+
    scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
    theme_figure()+
        theme(
          legend.position = "none"
        )

print(plt_081121)
```
now, figure out how to make pivot longer make TWO new columns (one with the mean and one with the sd), then add geom_errorbar(ymax = mean + sd, ymin = mean - sd)

# Dry air 3
```{r Lindt Dry Air Final }
data_082521 <- tbl %>% 
  filter (DATE == "2021-08-25")  %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-08-25 16:15:45" & MDT < "2021-08-25 17:30:34")

waterConcentration_plt(data_082521)
outletValve_plt(data_082521)

data_082521 <- data_082521 %>% 
  outlet_batches()

outlet_batch_plt(data_082521)

flask4_082521 <- data_082521 %>% 
  filter(MDT > "2021-08-25 16:27:15" & MDT < "2021-08-25 16:30:15") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 4)

flask12_082521 <- data_082521 %>% 
  filter(MDT > "2021-08-25 17:07:15" & MDT < "2021-08-25 17:10:15") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 12)

flask_ave_082521 <- data_082521 %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = c(2,3,5,6,7,8,9,10,11,13,14,15,16)) %>% 
  bind_rows(flask4_082521, flask12_082521) 
  

flask_ave_082521_plt <- Flask_h2o_plt(flask_ave_082521) 

print(flask_ave_082521_plt +  
        ylab(latex2exp::TeX('$H_2O (ppm)$')) +
        ggtitle("Lindt") +
       theme(plot.title = element_text(hjust = 0.5))
      )
```


# Water Vapor 2 
## March 20, 2022

```{r}
data_032022 <- tbl %>% 
  filter(DATE == "2022-03-20") %>% 
    BoulderTime() %>% 
      filter (MDT > "2022-03-20 09:45:00" & MDT < "2022-03-20 14:30:00") %>% 
        h2o_batches()


waterConcentration_plt(data_032022)

h2o_batch_plt(data_032022)
h2o_LastThreeMinutes(data_032022 %>% filter(H2O > 10000))

flasks_032022 <- data_032022 %>% 
  filter(H2O > 10000) %>% 
  flask_last3mintues() %>% 
  mutate(Flask = c(1:16)) 

flasks_032022 <- flasks_032022 %>% march182022_corr
```

## April 3, 2022

flasks 2 & 3 were super weird and plagued by condensation, so I just did 16 - 4 automatically 

13: 15:02 - 15:05 -- batch 180
3: 18:30 - 18:40
2: 18:48 - 18:54
```{r}
data_040322 <- tbl %>% 
  filter(DATE == "2022-04-03" | DATE == "2022-04-04") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-04-03 14:05:00" & MDT < "2022-04-03 19:00:00") %>% 
        h2o_batches()

waterConcentration_plt(data_040322)
d180_time_plt(data_040322)

h2o_batch_plt(data_040322)

data_040322 %>% 
  filter(MDT < "2022-04-03 17:50:00") %>%
  filter(H2O_Batch != 180) %>% 
  h2O_FirstThreeMinutes()

flasks_040322 <- data_040322 %>% 
  filter(MDT < "2022-04-03 17:50:00") %>% 
  filter(H2O_Batch != 180) %>% 
  flask_first3minutes() %>% 
  mutate(Flask = c(16:14, 12:4))

flask13 <- data_040322 %>% 
  filter(MDT > "2022-04-03 15:02:00" & MDT < "2022-04-03 15:05:00" ) %>% 
  flask_out_ave() %>% 
  mutate(Flask = 13)

flask3 <- data_040322 %>% 
  filter(MDT > "2022-04-03 18:30:00" & MDT < "2022-04-03 18:33:00" ) %>% 
  flask_out_ave() %>% 
  mutate(Flask = 3)


flask2 <- data_040322 %>% 
  filter(MDT > "2022-04-03 18:48:00" & MDT < "2022-04-03 18:54:00" ) %>% 
  flask_out_ave() %>% 
  mutate(Flask = 2)

flasks_040322 <- flasks_040322 %>% 
  bind_rows(flask13, flask3, flask2)

flasks_040322 <- flasks_040322 %>% April42022_corr
```
## Differences
```{r}
WVtest_results <- flasks_032022 %>% 
  left_join(flasks_040322, by = "Flask") %>% 
    mutate(
      d18O_diff_raw = d18O_out.y - d18O_out.x,
      d18O_diff_corr = d18O_corr.y - d18O_corr.x,
      d2H_diff =   d2H_out.y - d2H_out.x,
      d2H_diff_corr = d2H_corr.y - d2H_corr.x
    )

WVtest_results_plt <- WVtest_results %>% 
  pivot_longer(cols = c(d18O_diff_corr, d2H_diff_corr)) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode(
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(x = Flask, y = value, size = 2) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        geom_point()+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()+
        theme(
          legend.position = "none"
        )

print(WVtest_results_plt)
```

flasks 2 & 3 are for SURE weird. I feel pretty convinced there was a condensation problem; I should look for a water condensation problem in the first few flasks on Raclette.  Like the other boxes, it looks like there is ~ 0.75 per mil offset between the two time periods. Which would be really unexpected. check the standard runs that bracket this run. 
