---
title: "QAQC of Meringue"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---

#Setup
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path ("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     select(1, 2, 15, 17, 18, 19)
# 
# currentdate <- Sys.Date()
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))

```


# Dry Air 6/7/21 - 6/16/21 
(started at 22:37:39)

```{r DryAir1}
data_061621 <- tbl %>% 
  filter(DATE == "2021-06-16") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
    filter(MDT > "2021-06-16 16:37:35" & MDT <"2021-06-16 17:50:11")


WaterConcentration_plt(data_061621)
OutletValve_plt(data_061621)

data_061621 <- outlet_batches(data_061621)
plt_outlet_batch(data_061621)

flask5_061621 <- data_061621 %>% 
  filter (MDT > "2021-06-16 16:54:54" & MDT <"2021-06-16 16:57:54") %>% 
    flask_out_ave() %>% 
      mutate(Flask = 5)

flask11_061521 <- data_061621 %>% 
  filter (MDT > "2021-06-16 17:26:45" & MDT <"2021-06-16 17:27:59") %>% 
    flask_out_ave() %>% 
      mutate(Flask = 11)

flask_aves_061621 <- flask_ave_outlet(data_061621) %>% 
  mutate(Flask = c(2,3,4,6,7,8,9,10,12,13,14,15,16)) %>% 
  bind_rows(flask5_061621, flask11_061521)

Flask_h2o_plt(flask_aves_061621)
```
From this test:
6, 8, 11, 12 were targeted for repairs


# Dry Air 6/22/21-7/4/21 
(13:35:25)
```{r DryAir2}
data_070421 <- tbl %>% 
  filter(DATE == "2021-07-04") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-07-04 13:35:27" & MDT < "2021-07-04 14:50:17")

WaterConcentration_plt(data_070421)
OutletValve_plt(data_070421)

data_070421 <- outlet_batches(data_070421)
plt_outlet_batch(data_070421)

# flask5_070421 <- data_070421 %>%
#   filter(MDT >"2021-07-04 13:52:00" & MDT < "2021-07-04 13:55:00") %>%
#     flask_out_ave() %>%
#       mutate(Flask = 5)

# flask11_070421 <- data_070421 %>%
#   filter(MDT >"2021-07-04 13:22:00" & MDT < "2021-07-04 13:25:00") %>%
#     flask_out_ave() %>%
#       mutate(Flask = 11)

flask_aves_070421 <- flask_ave_outlet(data_070421) %>% 
  mutate(Flask = c(2,3,4,5,6,7,8,9,10,11, 12,13,14,15,16)) 

Flask_h2o_plt(flask_aves_070421)
```
6, 8, 12 all got a lot better. 

8,11,12 still have problems 


# Water Vapor: 7/19/2021 - 08/02/2021
```{r}
data_071922 <-  tbl %>% 
  filter(DATE == "2021-07-19")
```


```{r 080221_H2O}
data_080221 <- tbl %>% 
  filter(DATE == "2021-08-02")  %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT < "2021-08-02 14:56:50") %>% 
        outlet_batches()

WaterConcentration_plt(data_080221)
plt_outlet_batch(data_080221)

flask_aves_080221 <- flask_ave_outlet(data_080221) %>% 
  filter(H2O_out >1600) %>% 
    mutate(Flask = c(2:16))

Flask_isotopes_plt(flask_aves_080221)
```
8 & 11 are still having a bad time 

```{r DualIsotope}
dual_isotope_plt(flask_aves_080221)
```


# Dry Air: 8/15/2021 - 08/22/2021
```{r DryAir3}
data_082221 <- tbl %>% 
  filter(DATE == "2021-08-22")  %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number())  %>% 
      filter(MDT > "2021-08-22 11:49:48" & MDT < "2021-08-22 13:05:17") %>% 
  outlet_batches()
 
WaterConcentration_plt(data_082221)
OutletValve_plt(data_082221)

plt_outlet_batch(data_082221)

manual_flasks_082221 <- data_082221 %>% 
  filter(MDT > "2021-08-22 12:06:21" & MDT < "2021-08-22 12:09:21") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 5)

manual_flasks_082221 <- manual_flasks_082221 %>% 
  bind_rows(
    data_082221 %>% 
      filter(MDT > "2021-08-22 12:36:45" & MDT < "2021-08-22 12:39:45") %>% 
        flask_out_ave() %>% 
          mutate(Flask = 11)
  )

flask_aves_082221 <- flask_ave_outlet(data_082221) %>% 
  mutate(Flask = c(2,3,4,6,7,8,9,10,12,13,14,15,16)) %>% 
  bind_rows(manual_flasks_082221)

Flask_h2o_plt(flask_aves_082221)
```
5, 11, 12 still aren't great. 2 is also a bit of a worry. 



# Dry Air: 08/25/2021 - 09/01/2021

```{r DryAir4}
data_090121 <- tbl %>% 
  filter(DATE == "2021-09-01")  %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT < "2021-09-01 11:10:00" & MDT > "2021-09-01 09:53:18") %>% 
        outlet_batches()

WaterConcentration_plt(data_090121)
OutletValve_plt(data_090121)
plt_outlet_batch(data_090121)

manual_flasks_090121 <- data_090121 %>% 
  filter(MDT > "2021-09-01 10:39:51" & MDT < "2021-09-01 10:42:51") %>% 
  flask_out_ave() %>% mutate(Flask =11)

manual_flasks_090121 <- manual_flasks_090121 %>% 
  bind_rows(
    data_090121 %>% 
  filter(MDT > "2021-09-01 11:04:51" & MDT < "2021-09-01 11:07:51") %>% 
  flask_out_ave() %>% mutate(Flask =16)
  )

flask_aves_090121 <- flask_ave_outlet(data_090121) %>% 
  mutate(Flask = c(2:10, 12:15)) %>% 
  bind_rows(manual_flasks_090121)

Flask_h2o_plt(flask_aves_090121)
```

# 14 Day Water Vapor Tests 
## March 17 - March 31 
#### in


```{r March 17, 2022}
data_031722 <- tbl %>% 
  filter(DATE == "2022-03-17" | DATE == "2022-03-18") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-03-17 11:31:00" & MDT < "2022-03-17 15:15:00") %>% 
        outlet_batches() %>% 
          h2o_batches()
  
#From this series of plots its easy to see that using an h2o batch plot will be much easier here
waterConcentration_plt(data_031722) 
h2o_batch_plt(data_031722)

outletValve_plt(data_031722)
outlet_batch_plt(data_031722)

#double check that your groups are clean
h2o_lastthreeminutes(data_031722)
  
#need to average batches 75 & 540 by hand   
flask3_031722 <- data_031722 %>% 
  filter(H2O_Batch == 75) %>% 
    group_by(H2O_Batch) %>% 
    mutate( 
      row = row_number(),
      totalrows= n()
    ) %>% 
    filter (totalrows > 100 & row < (totalrows - 85) & row > (totalrows - 310)) %>% 
      flask_out_ave() %>% 
        mutate(Flask = 3)

#since this is the last flask, if i edit the data frame at all, this needs to be edited
flask14_031722 <- data_031722 %>% 
  filter(H2O_Batch == 540) %>% 
    group_by(H2O_Batch) %>% 
      mutate(
        row = row_number(),
        totalrows = n(),
      ) %>% 
        filter(totalrows > 100 & row < (totalrows - 200) & row > (totalrows - 425)) %>% 
        flask_out_ave() %>% 
          mutate(Flask = 14)
  
flasks_031722 <- data_031722 %>% 
  filter (H2O_Batch != 75 & H2O_Batch != 540) %>% 
    flask_last3mintues() %>% 
      mutate(Flask = c(2, 4:13)) %>% 
        bind_rows(flask3_031722, flask14_031722) %>% 
        march182022_corr()
```
### out 

I am playing with my new averaging functions for the first time, so I did this in two chunks. I started with the second half of the day which was more straight forward, and then tackled the first half of the day. It's important to note that for flasks 16 - 13 I was using  a dry air pressure that was WAY too high for the Mass flow controller, and so there was a big influx of dry air into the flasks first thing. I used the step down from the vapor system mass flow controller to help with that problem, and that made my life WAY better. You can see how that problem shows up in the water concentration data in the first 2 minutes of each measurement. 
```{r March 31, 2022}

data_033122_secondhalf <- tbl %>% 
  filter(DATE == "2022-03-31") %>% 
  BoulderTime()  %>% 
    filter(MDT > "2022-03-31 13:30:00")  %>%
      outlet_batches() %>% 
        h2o_batches()

waterConcentration_plt(data_033122_secondhalf)
h2o_batch_plt(data_033122_secondhalf)

h2O_FirstThreeMinutes(data_033122_secondhalf %>% filter(H2O > 5000))

# I was curiosu if the way i cut up the data would change d18O averages at all 
d18O_plt <- data_033122_secondhalf %>% 
  ggplot()+
  aes(x = MDT, y = Delta_18_16, color = H2O_Newbatch)+
  geom_point() +
  theme_figure()+
  theme(legend.position = "none")

ggplotly(d18O_plt, dynamicTicks = TRUE)

# it doesn't!

flasks_033122_secondhalf <- data_033122_secondhalf %>% 
  filter(H2O > 1000) %>% 
  flask_first3minutes() %>% 
  mutate(Flask = c(9,8,7,6,5,4, 3, 2))


data_033122_firsthalf <- tbl %>% 
  filter(DATE == "2022-03-31") %>% 
  BoulderTime() %>% 
  filter(MDT < "2022-03-31 12:10:00") %>% 
  h2o_batches() %>% 
  filter(H2O > 5000)


waterConcentration_plt(data_033122_firsthalf)
h2o_batch_plt(data_033122_firsthalf %>% 
                filter(H2O_Batch!=45 &  H2O_Batch != 261 & H2O_Batch != 362 & H2O_Batch != 482))

h2O_FirstThreeMinutes(data_033122_firsthalf %>% 
                filter(H2O_Batch!=45 & H2O_Batch != 261 & H2O_Batch != 362 & H2O_Batch != 482))


flasks_033122_firsthalf <- data_033122_firsthalf %>% 
  filter(H2O_Batch!=45 & H2O_Batch != 261 & H2O_Batch != 362 & H2O_Batch != 482) %>% 
    flask_first3minutes() %>% 
      mutate(Flask = c(15,14,13,12,11,10))

flask16_033122 <- data_033122_firsthalf %>% 
  filter(MDT > "2022-03-31 09:43:00" & MDT < "2022-03-31 09:46:00") %>% 
    flask_out_ave() %>% 
      mutate(
        H2O_Batch = 45,
        Flask = 16
      )
   
FlaskOut_033122 <- bind_rows(
  flask16_033122,
  flasks_033122_firsthalf,
  flasks_033122_secondhalf
) %>% April42022_corr()

```

### diff

```{r}
WVtest_results <- flasks_031722 %>% 
  left_join(FlaskOut_033122, by = "Flask") %>% 
    mutate(
      d18O_diff = d18O_corr.y - d18O_corr.x,
      d2H_diff =   d2H_corr.y - d2H_corr.x
    )


WVtest_results_plt <- WVtest_results %>% 
  pivot_longer(cols = c(d18O_diff, d2H_diff)) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode(
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(x = Flask, y = value, size = 2) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        geom_point()+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()+
        theme(
          legend.position = "none"
        )

print(WVtest_results_plt)
```





# May 2022 Backyard test 

```{r}
may24 <- tbl %>% 
  filter(DATE == "2022-05-24" | DATE == "2022-05-25") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-05-24 15:45")

waterConcentration_plt(may24)
d180_time_plt(may24)
```


```{r}
May2022_data <- tibble(
  Flask = (16:2),
  T = c(27,25,22, 18,17,15, 20,20.6,21.6, 25,27,28, 21,21,21),
  d18O = c(-31.85, -17.87, -24.33, -31.85, -17.91, -23.39, -32.76,-18.09, - 26.27, -33.9, -18.09, -23.43, -33.4, -19.0, -23.3),
  d18O_corr = (11.45 - 0.0795*T + 1.0012*d18O),
  d2H = c(-251,-167.4, -191.2, -247.8,-168, -195, -265.1,-168.7, - 207, -262, - 169.5, -192.2, -255.6, -173.5,  - 189),
  d2H_corr = (104.96 - 1.0342*T + 1.0724*d2H),
  water= c("Light", "Atmosphere", "DI", "Light", "Atmosphere", "DI", "Light", "Atmosphere", "DI","Light", "Atmosphere", "DI", "Light", "Atmosphere", "DI" )
) 


# %>% 
#   pivot_longer(cols = c(d18O, d2H)) %>% 
#   mutate(
#       # turn into ordered variable (factor) that keeps the order
# 
#       latex_name = as_factor(name) %>% fct_inorder()  %>%
#         # introduce latex substitutions
#         fct_recode(
#                    "$\\Delta \\delta^2H" = "d2H",
#                    "$\\Delta \\delta^{18}O" = "d18O")
#     ) 


# May2022_data %>%  ggplot()+
#         aes(x = Flask, y = value,  fill = water) +
#         facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
#         geom_point(pch = 21, size = 4)+
#         scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
#         theme_figure()+
#         theme(
#           legend.position = "none",
#           axis.title.y = element_blank()
#         ) +
#         scale_fill_viridis(option = "C", discrete = TRUE)



d18O_plt <- May2022_data %>% 
  ggplot()+
  aes(x = Flask, y = d18O_corr, fill = water)+
  geom_errorbar(aes(ymin = d18O_corr - 0.5, ymax = d18O_corr+0.5)) +
  geom_point(pch = 21, size = 4)+
  geom_hline(aes(yintercept = - 8.5), linetype = "longdash") +
  geom_hline(aes(yintercept = - 8.0), linetype = "dotted") +
  geom_hline(aes(yintercept = - 9.0), linetype = "dotted") +
  
  geom_hline(aes(yintercept = -13.82), linetype = "longdash") +  
  geom_hline(aes(yintercept = -14.32), linetype = "dotted") +
  geom_hline(aes(yintercept = -13.32), linetype = "dotted") +
  
  geom_hline(aes(yintercept = -22.69), linetype = "longdash")+
  geom_hline(aes(yintercept = -22.19), linetype = "dotted")+
  geom_hline(aes(yintercept = -23.19), linetype = "dotted") +
  
  scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
  theme_figure() +
  labs(
   y = latex2exp::TeX("$\\Delta\\delta^{18}O$")) +
  scale_fill_viridis(option = "C", discrete = TRUE)

print(d18O_plt)


d2H_plt <- May2022_data %>% 
   filter(water == "DI") %>%
  ggplot()+
  aes(x = Flask, y = d2H_corr, fill = water)+
  geom_errorbar(aes(ymin = d2H_corr - 2.4, ymax = d2H_corr+2.4)) +
  geom_point(pch = 21, size = 4)+
  geom_hline(aes(yintercept = -96.8832), linetype = "longdash") +
  geom_hline(aes(yintercept = -99.28), linetype = "dotted") +
  geom_hline(aes(yintercept = -94.4832), linetype = "dotted") +

  geom_hline(aes(yintercept = -130.0204), linetype = "longdash") +
  geom_hline(aes(yintercept = -132.4204), linetype = "dotted") +
  geom_hline(aes(yintercept = -127.62), linetype = "dotted") +

  geom_hline(aes(yintercept = -199.5119), linetype = "longdash")+
  geom_hline(aes(yintercept = -201.9119), linetype = "dotted")+
  geom_hline(aes(yintercept = -197.1119), linetype = "dotted") +
  
  scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
  theme_figure() +
  labs(
   y = latex2exp::TeX("$\\Delta\\delta^2H$")) +
  scale_fill_viridis(option = "C", discrete = TRUE)

print(d2H_plt)
```