---
title: "Oglala National Grassland data"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---


```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
## load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)
library(gridExtra)
library(egg)
library(readxl)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))
source(file.path("scripts", "corrections.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

tbl <- readRDS(file.path("data","2022Data.RDS"))
```

# Deployment 1
Measuring Lindt which was deployed in Oglala National Grassland 
Photon: SWISS-5. No data log, because it was full

Sample dates:
*June 25: Flasks 2-4
*June 29: Flasks 5-7
*July 4: Flasks 8 - 10
*July 9: Flasks 11-13
*July 14: Flasks 14-16

Picked up from the field on August 1 

## August 5, 2022

July 6, 2023 -> adjusted time zone to run in pacific time zone
```{r}
data_080522 <- tbl %>% 
  filter(DATE == "2022-08-05") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-08-05 9:30" & MDT < "2022-08-05 13:30") %>% 
        h2o_batches()

h2o_batch_plt(data_080522)

flask16 <- data_080522 %>% 
  filter(MDT > "2022-08-05 9:44" & MDT < "2022-08-05 9:49") %>% flask_out_ave() %>% mutate(Flask = 16) 

flask15 <- data_080522 %>%  
  filter(MDT > "2022-08-05 10:09" & MDT < "2022-08-05 10:14") %>% 
  flask_out_ave() %>% mutate(Flask = 15)

flask14 <- data_080522 %>% filter(H2O_Batch == 176)%>%  
  filter(MDT > "2022-08-05 10:41" & MDT < "2022-08-05 10:46") %>%
  flask_out_ave() %>% mutate(Flask = 14)

flask13 <- data_080522 %>% filter(H2O_Batch==215) %>%  flask_first3minutes() %>% mutate(Flask = 13)

flask12 <- data_080522 %>% filter(H2O_Batch == 249) %>% filter(MDT > "2022-08-05 11:23" & MDT < "2022-08-05 11:28") %>%
  flask_out_ave() %>% mutate(Flask = 12)

flask11 <- data_080522 %>% filter(H2O_Batch == 352) %>% filter(MDT > "2022-08-05 12:00" & MDT < "2022-08-05 12:05") %>%
  flask_out_ave() %>% mutate(Flask = 11)

flask10 <- data_080522 %>% filter(H2O_Batch == 387) %>% filter(MDT > "2022-08-05 12:18" & MDT < "2022-08-05 12:23") %>%
  flask_out_ave() %>% mutate(Flask = 10)

flask9 <- data_080522 %>% filter(H2O_Batch == 426) %>% filter(MDT > "2022-08-05 12:45" & MDT < "2022-08-05 12:50") %>%
  flask_out_ave() %>% mutate(Flask = 9)

flask8 <- data_080522 %>% filter(H2O_Batch == 537) %>% filter(MDT > "2022-08-05 13:20" & MDT < "2022-08-05 13:25") %>%
  flask_out_ave() %>% mutate(Flask = 8)

flasks_0805 <- bind_rows(flask16, flask15, flask14, flask13, flask12, flask11, flask10, flask9, flask8) %>% 
  mutate(
    sampledate = ifelse(Flask > 13, "2022-07-14",
                        ifelse(Flask == 13 |Flask == 12 | Flask ==11, "2022-07-09", "2022-07-04")),
    sampledepth = c(75,50,25,75,50,25,75,50,25),
    Analyst = "Rachel"
  )

```

## August 8, 2022
July 6, 2023 updated time zones
```{r}
data_080822 <- tbl %>% 
  filter(DATE == "2022-08-08") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-08-08 15:15" & MDT < "2022-08-08 16:15") %>% 
  h2o_batches()

h2o_batch_plt(data_080822)
h2O_FirstThreeMinutes(data_080822)

flasks_0808 <- data_080822 %>% 
  filter(H2O > 5000) %>% flask_first3minutes() %>% 
  mutate(
    Flask = c(7:5),
    sampledate = "2022-06-29",
    sampledepth = c(75,50,25)
  )
```

## August 9, 2022
```{r}
data_0809 <- tbl %>% 
  filter(DATE == "2022-08-09") %>% 
  BoulderTime() %>% 
  filter(MDT> "2022-08-09 08:57" & MDT < "2022-08-09 9:47") %>% 
  h2o_batches()

h2o_batch_plt(data_0809)

flasks0809 <-  data_0809 %>% filter(H2O >10000) %>% flask_first3minutes() %>% 
  mutate(
    Flask = c(4:2),
    sampledate = "2022-06-25",
    sampledepth = c(75,50,25)
  )
```

## Combine and plot
Updated the correction on July 6, 2023
```{r}
oglala_firstround <- bind_rows(flasks_0805, flasks_0808, flasks0809) %>% 
  mutate(
    T = c(22,22.8,23, 22,22.8,23, 22,23,25, 21.3,22.8,25, 21.5,22.8,23),#temps from data logger! estimated for 7-9 and 7-14 becuase the temp logger was corrupted 
    d18O_liq = 11.45 - 0.0795*T +1.0012*d18O_out,
    d2H_liq =104.96 - 1.0342*T + 1.0724*d2H_out,
    
    d18O_vsmow = round( ((d18O_liq - 0.3336484) / 1.0072042),1),
    d2H_vsmow = round( ((d2H_liq - -7.408711) / 1.008137), 1),
    
    
    d18o_offset =  d18O_vsmow - 0.9,
    d2H_offset =  d2H_vsmow - 2.6,
    
    dexcess = d2H_offset - 8*d18o_offset
  )


oglala_firstround %>% 
  mutate(
    Site = "Oglala Ntl. Grassland"
  ) %>% 
    dplyr::select(Site, sampledate, sampledepth, Flask, T, d18o_offset, SD_18O_out, d2H_offset, SD_2H_out) %>% 
      arrange(Flask) %>% 
        rename(Date = sampledate, Depth = sampledepth, AnalyticalError = SD_18O_out) 

# %>% 
#         write.csv("output/OglalaJuneData.csv")

```


```{r}
oglala_d18o <- oglala_firstround %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Oglala National Grassland, NE")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18o_offset - 0.5,
    ymin = d18o_offset + 0.5,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18o_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )
  
print(oglala_d18o)
```




```{r}
oglala_d2H <- oglala_firstround %>% 
  #filter(sampledepth == 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure() +
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )
  
print(oglala_d2H)
```

```{r Oglala July 2022}
ggarrange(oglala_d18o,oglala_d2H)
```

```{r}
crossplt <- oglala_firstround %>% 
  ggplot()+
  geom_abline(intercept = 10, slope = 8, size = 2, linetype = "longdash")+
  geom_errorbar(aes(
    x = d18o_offset,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = d2H_offset,
    xmax = d18o_offset - 0.9,
    xmin = d18o_offset + 0.9,
    height = 0)) +
  geom_point(
    aes(
      x = d18o_offset, 
      y = d2H_offset, 
      pch = factor(sampledepth),
      fill = factor(sampledate),
      shape = factor(sampledepth)),
    size = 6
  )+
  scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  theme_figure()

crossplt
```


```{r}
oglala_dexcess <- oglala_firstround %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_errorbar(aes(x = sampledate, ymax =  dexcess + 3.5, ymin = dexcess - 3.5, width = 0))+
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(oglala_dexcess)
```


# Deployment 2
```{r}
Sept22 <- read_excel("data/Oglala_Sept2022.xlsx")

Sept22 <- Sept22 %>% 
  mutate(
    sampledate = ymd(SampleDate),
    T = c(21,21.5,21.5,19,20,20),
    d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O,
    d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H,
    
    d18O_vsmow = (d18O_rothfuss - 0.711) / 1.018,
    d2H_vsmow = (d2H_rothfuss - -0.4566) / 1.0297,
    
    d18o_offset =  round(d18O_vsmow - 0.9, 1),
    d2H_offset =  round(d2H_vsmow - 2.6,1),
    
    dexcess = d2H_offset - 8*d18o_offset
  )

```

```{r}
oglala_d18o_0922 <- Sept22 %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Oglala National Grassland, NE")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18o_offset - 1.0,
    ymin = d18o_offset + 1.0,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18o_offset,
      pch = as.factor(SampleDepth),
      fill = as.factor(SampleDepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure() +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )
  
print(oglala_d18o_0922)



oglala_d2H_0922 <- Sept22 %>% 
  #filter(sampledepth == 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_offset,
      pch = as.factor(SampleDepth),
      fill = as.factor(SampleDepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure() +
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )
  
print(oglala_d2H_0922)


oglala_dexcess_0922 <- Sept22 %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_errorbar(aes(x = sampledate, ymax =  dexcess + 3.5, ymin = dexcess - 3.5, width = 0))+
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(SampleDepth),
      fill = as.factor(SampleDepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(oglala_dexcess_0922)
```

```{r}
ggarrange(oglala_d18o_0922,oglala_d2H_0922)
```

```{r}
Sept22 <- Sept22 %>% 
  rename(
    sampledepth = "SampleDepth"
  )

oglala_firstround$sampledate <- as.Date(oglala_firstround$sampledate)


all2022 <- bind_rows(oglala_firstround, Sept22)

```


```{r}
O_stream <- read.csv("data/Precipitation_data/1687210317-data.csv") %>% 
  mutate(month = month(Collection_Date)) %>% 
  filter(d18O < 900) %>% 
  filter(Type != "Lake") %>% 
  mutate(month = month(Collection_Date))

```



```{r}
crossplt_0922 <- all2022 %>%
  ggplot()+
  annotate("rect", xmax = -8.6, xmin = -10.2, ymax =40, ymin = -200, alpha = 0.5, fill = "#D53E3E") +
  geom_abline(intercept = -7.346027 , slope = 7.189599, size = 1, linetype = 1 ) +
  geom_abline(intercept = 10, slope = 8, size = 1, linetype = 3) +
  geom_point(data = O_stream, aes(x = d18O, y = d2H,), shape = 23, fill = "#cecece" ) +
  
  
  geom_errorbar(aes(
    x = d18o_offset,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = d2H_offset,
    xmax = d18o_offset - 1.0,
    xmin = d18o_offset + 1.0,
    height = 0)) +
  geom_point(
    aes(
      x = d18o_offset, 
      y = d2H_offset, 
      pch = factor(sampledepth),
      color = factor(sampledate),
      shape = factor(sampledepth)),
    size = 5
  )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  scale_y_continuous(limits = c(-200, 40), expand = c(0,0))+
  scale_x_continuous(limits = c(-25, 5), expand = c(0,0))+
  theme_figure()

crossplt_0922

```



final_data <- ClumpedData %>% 
  filter(Project == "REH") %>% 
  dplyr:: select(
    Sample.ID,
    Strat_height_m,
    d13C.avg,
    d13C.2se,
    d18O.avg,
    d18O.2se,
    D47.90.avg,
    D47.se,
    T.A,
    T.A.2se,
    d18Ow.A,
    d18Ow.A.2se


```{r}
finaltbl <- all2022 %>% 
  mutate(site = "Oglala") %>% 
  dplyr::select(
    site, 
    sampledate,
    sampledepth,
    d18o_offset,
    d2H_offset,
    dexcess
  ) %>% 
  rename(
    "Site" = site,
    "Sample Date" = sampledate,
    "Sample Depth (cm)" = sampledepth,
    "d18O (VSMOW)" = d18o_offset,
    "d2H (VSMOW)" = d2H_offset,
    "d-excess ()" = dexcess
  )

write.csv(finaltbl, "output/OglalaResults_ch3.csv")
```

  