---
title: "QAQC of Raclette"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console # change to inline to show output inline
---

#Setup
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
l# load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#Load 2021 data
tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Dry Air 1, July 27, 2021

```{r}
data_072721 <- tbl %>% 
  filter(DATE == "2021-07-27") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-07-27 09:35:00" & MDT < "2021-07-27 11:14:19" ) %>% 
  outlet_batches()

WaterConcentration_plt(data_072721)
plt_outlet_batch(data_072721)

flask_aves_072721 <- data_072721 %>% 
  flask_ave_outlet() %>% 
  filter(batch != 11) %>% 
  mutate(Flask = c(2:9, 11:15))


#Manually separate flasks 10, 12, 16 
manual_flasks_072721 <- data_072721 %>% 
  filter (MDT > "2021-07-27 10:27:18" & MDT <"2021-07-27 10:34:00") %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = 10)

manual_flasks_072721 <- manual_flasks_072721 %>% 
  bind_rows(
    data_072721 %>% 
  filter (MDT > "2021-07-27 11:06:49" & MDT <"2021-07-27 11:14:11") %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = 16)
  )

flask_aves_072721 <- flask_aves_072721 %>% 
  bind_rows(manual_flasks_072721)


Flask_h2o_plt(flask_aves_072721)
```


# Water Vapor, August 1 - August 18, 2021 
 **INPUT VALUES**
 Here, I just picked three peaks, all about an hour apart, averaged their value for the last 2 minutes of filling. After seeing they were all well within error of each other, I averaged them and that's what I'm calling my 'input' value. 
 
 Because I was also simultaneously testing the SMC code, every third flask was filled with dry air 
```{r input values}
data_080121 <- tbl %>% 
  filter(DATE == "2021-08-01") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number())  %>% 
      filter(MDT > "2021-08-01 13:52:00") 

WaterConcentration_plt(data_080121)


inputvalue1 <- data_080121 %>% 
  filter(MDT > "2021-08-01 16:07:26" & MDT < "2021-08-01 16:09:26") %>% 
  flask_out_ave()
  

inputvalue1 <- inputvalue1 %>% 
  bind_rows(
    data_080121 %>% 
  filter(MDT > "2021-08-01 15:24:30" & MDT < "2021-08-01 15:26:30") %>% 
  flask_out_ave()
  )

inputvalue1 <- inputvalue1 %>% 
  bind_rows(
    data_080121 %>% 
  filter(MDT > "2021-08-01 17:20:00" & MDT < "2021-08-01 17:22:00") %>% 
  flask_out_ave()
  )

refvalues_080121 <- tibble(
  d18O_in_0801 = round(mean(inputvalue1$d18O_out),2),
  SD_d18O_in = round(mean(inputvalue1$SD_18O_out),2),
  d2H_in_0801 = round(mean(inputvalue1$d2H_out),2),
  SD_d2H_in = round(mean(inputvalue1$SD_2H_out ),2)
)

refvalues_080121_plt <- refvalues_080121 %>% 
  ggplot()+
  aes(x = d18O_in_0801, y = d2H_in_0801 )+
  geom_point(aes(color = "red", size = 2))+
  geom_errorbar(aes(ymin = d2H_in_0801 - SD_d2H_in, ymax = d2H_in_0801 + SD_d2H_in), width = 0)+
  geom_errorbarh(aes(xmin = d18O_in_0801 - SD_d18O_in, xmax = d18O_in_0801 + SD_d18O_in), height = 0)


```

*unzipped this box*
```{r}
data_081821 <- tbl %>% 
  filter(DATE == "2021-08-18") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-08-18 10:33:00" & MDT <"2021-08-18 13:18:16") %>% 
        outlet_batches()

WaterConcentration_plt(data_081821)
plt_outlet_batch(data_081821 %>% 
                   filter(newbatch != 7 & 
                          newbatch!=16 & 
                          newbatch !=25 & 
                          newbatch!=38 & 
                          newbatch !=46 & 
                          newbatch !=51 & 
                          newbatch !=61 &
                          newbatch !=73 &
                          newbatch !=87 &
                          newbatch !=99 &
                          newbatch !=111 &
                          newbatch !=119 )
                 )

flask_aves_081821 <- flask_ave_outlet(data_081821) %>% 
  filter(batch != 7 & 
           batch != 16 & 
           batch != 25 & 
           batch != 38 &
           batch != 46 &
           batch != 51 &
           batch != 61 &
           batch != 73 &
           batch != 87 &
           batch !=99 &
           batch !=111 &
           batch !=119 ) %>% 
    mutate(Flask = c(16:12, 12, 11:2))

Flask_h2o_plt(flask_aves_081821 %>% 
                filter (H2O_out < 10000))

dual_isotope_plt(flask_aves_081821 %>% 
                   filter(H2O_out > 10000))


plt_081821 <- flask_aves_081821 %>% 
  filter(H2O_out >10000) %>% 
    ggplot()+
      aes(x = d18O_out, y = d2H_out)+
      geom_point(aes(size =2, text = Flask )) +
        geom_errorbar(aes(ymin = d2H_out + SD_2H_out, ymax = d2H_out - SD_2H_out))+
        geom_errorbarh(aes(xmin = d18O_out + SD_18O_out, xmax = d18O_out - SD_18O_out)) +
      geom_point(data = refvalues_080121, aes(x = d18O_in_0801, y = d2H_in_0801, color = "red", size = 2)) +
        theme_figure()+
        theme(
          legend.position = "none"
      )

ggplotly( plt_081821)        
print(plt_081821)
```
2, 6, 10, 11, 12, all look bad. I'm not encouraged that they're all kind of bad though

Did repairs on the 25th of august

# Dry Air 2, August 25 - September 1, 2021 
```{r}
data_090121 <- tbl %>% 
  filter(DATE == "2021-09-01") %>% 
    mutate(UTC = hms(TIME), #by using the lubridate hms, it makes the UTC time filterable with dplyr
           UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
           MDT = with_tz(UTC_full, tzone = "America/Denver"),
           seconds = row_number()) %>% 
      filter(MDT > "2021-09-01 11:16:09" & MDT <"2021-09-01 12:32:21") %>% 
        outlet_batches()

WaterConcentration_plt(data_090121)
plt_outlet_batch(data_090121)

flask_aves_090121 <- flask_ave_outlet(data_090121) %>% 
  mutate(Flask = c(2:16))
Flask_h2o_plt(flask_aves_090121)
```
2, 6, 10, 11, 12 all still suck. 

# Water Vapor Test 
## March 20, 2022
```{r}
data_032022 <- tbl %>% 
  filter(DATE == "2022-03-20" | DATE == "2022-03-21") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-20 17:20:00" & MDT < "2022-03-20 21:42:00") %>% 
  h2o_batches()

waterConcentration_plt(data_032022)

data_032022 %>% 
  filter(H2O > 7000) %>% 
  h2o_batch_plt()

data_032022 %>%  
  filter(H2O>7000) %>% 
  h2o_LastThreeMinutes() 

flasks_032022 <- data_032022 %>%  
  filter(H2O>7000) %>%
  flask_last3mintues() %>% 
  mutate(Flask = c(1:16))
```

## April 3, 2022
I did this in two parts - from 7:03 pm to 10:30 pm, and then another session the next morning
I never flipped away from port 16, so it was open to atm for the whole test period.


on april 3, batch 205 & 345 are both weird with water condensation problems 
these are flasks 14, 11

I averaged over a longer time period (5 minutes) for flask 14
I averaged over a shorter time period for flask 11 (2 mintes) 39-41
```{r}
data_040322 <- tbl %>% 
  filter(DATE == "2022-04-04") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-03 19:00:00" & MDT < "2022-04-03 22:34:00") %>% 
  h2o_batches()

waterConcentration_plt(data_040322) 
data_040322 %>% h2o_batch_plt()
data_040322 %>% 
  filter(H2O_Batch !=58 & H2O_Batch != 205 & H2O_Batch !=345) %>% 
    h2O_FirstThreeMinutes()

flasks_040322 <- data_040322 %>% 
  filter(H2O_Batch !=58 & H2O_Batch != 205 & H2O_Batch !=345) %>%
  flask_first3minutes() %>% 
  mutate(Flask = c(16,15,13,12,10:5))

flask14 <- data_040322 %>% 
  filter(MDT > "2022-04-03 19:48:00" & MDT < "2022-04-03 19:53:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 14)

flask11 <- data_040322 %>% 
  filter(MDT > "2022-04-03 20:39:00" & MDT < "2022-04-03 20:41:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 11)


flasks_040322 <- flasks_040322 %>% 
  bind_rows(flask14, flask11)
```


```{r}
data_040422 <- tbl %>% 
  filter(DATE == "2022-04-04") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-04-04 07:32:00" & MDT < "2022-04-04 08:30:00") %>% 
  h2o_batches()

waterConcentration_plt(data_040422)
d180_time_plt(data_040422)
h2o_batch_plt(data_040422)
h2O_FirstThreeMinutes(data_040422 %>% filter(H2O > 5000))

flasks_040422 <- data_040422 %>% 
  filter(H2O > 5000) %>% 
  flask_first3minutes() %>% 
  mutate(Flask = c(4,3,2))

allflasks <- flasks_040322 %>% bind_rows(flasks_040422)
```

```{r}
WVtest_results <- flasks_032022 %>% 
  left_join(allflasks, by = "Flask") %>% 
    mutate(
      d18O_diff = d18O_out.y - d18O_out.x,
      d2H_diff =   d2H_out.y - d2H_out.x
    )

WVtest_results_plt <- WVtest_results %>% 
  pivot_longer(cols = c(d18O_diff, d2H_diff)) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode(
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(x = Flask, y = value, size = 2) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        geom_point()+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()+
        theme(
          legend.position = "none"
        )

print(WVtest_results_plt)
ggplotly(WVtest_results_plt)


evap <- WVtest_results %>% 
  ggplot()+
  aes(x = d18O_diff, y = d2H_diff) +
  geom_point()+
  geom_smooth(method = "lm")+
  theme_figure()

print(evap)

lm(formula = d2H_diff ~ d18O_diff, data = WVtest_results)
```



