---
title: "Rosti QAQC"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: no # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---
# Setup
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#Load 2021 data
tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# Fall 2020 Testing
* During this round of testing, I had tephlon swagelok fittings w/ ptfe 1/8" tubing running from the flasks to the valco valve. Becuase of the results below, we decided to not use that. 

* Because the main round of testing was done w/ the PTFE stuff, I think its probably best if I replicate again  
```{r}
rosti <- read_csv("data/2021Data/Fall_2020_SWISS_tests.csv")

rosti <- rosti %>% mutate (
  h2o_in = 11590,
  d18O_in = -13.17,
  d2h_in = -112.5,
  d18O_diff = d18O_in - wet_test_d180,
  d2H_diff = d2h_in - wet_test_d2H,
  toowet = ifelse(dry_test_1 > 2500 | dry_test_2 > 2500, TRUE, FALSE)
)
```

```{r}
rosti_plot <- rosti %>% 
  pivot_longer(c(dry_test_1, dry_test_2, d18O_diff, d2H_diff)) %>% 
  ggplot () +
  aes (x = Port, y = value)+
  geom_point() +
  facet_wrap(
    ~name, 
    scales = "free")+
  theme_bw()


rosti_plot
ggplotly(rosti_plot)

DryAir_labs <- c("9-day dry air test", "27-day dry air test")
names(DryAir_labs) <- c("dry_test_1", "dry_test_2")

otherlab <- c ("H2O concentration")
names(otherlab) <- c("value")

rosti_dry <- rosti %>% 
  pivot_longer(c(dry_test_1, dry_test_2)) %>% 
  ggplot () +
  aes(
    x = Port, 
    y = value, 
    color = ifelse(value > 1000 , 'red', 'black') 
  )+
  geom_point(size = 3) +
  geom_hline(yintercept = 1000)+
  facet_wrap(
    ~name,
    labeller = labeller(name = DryAir_labs))+
  theme_figure()+
  theme(
    legend.position = "none"
  )

ggplotly(rosti_dry)
```

In May 2021 I put Rosti out in Briggsdale to do an early field-test deployment. What I learned after that deployment:
1. The N2 tank ran out before I could do a full run-through
1. The valco valve got misaligned. I had to 'train' the valco valve again back in the lab using the home button.
1. Flasks 8, 9 , 10 were not ready for field deployment after I had replaced the tephlon with stainless steel, so those were of significant concern during the following dry air tests

# 8 day Dry Air 
```{r}
data_072821 <- tbl %>% 
  filter (DATE == "2021-07-28") %>% 
    mutate(
      UTC = hms(TIME),
      UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
      MDT = with_tz(UTC_full, tzone = "America/Denver"),
      seconds = row_number()
    ) %>% 
      filter(MDT > "2021-07-28 09:21:37" & MDT < "2021-07-28 10:37:36") %>% 
        outlet_batches()

waterConcentration_plt(data_072821)
outlet_batch_plt(data_072821)

manual_flasks_072821 <- data_072821 %>% 
  filter(MDT > "2021-07-28 10:11:48" & MDT < "2021-07-28 10:16:42") %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = 11)

flask_aves_072821 <- flask_ave_outlet(data_072821) %>% 
  mutate(Flask = c(2:10, 12:16)) %>% 
  bind_rows(manual_flasks_072821)

Flask_h2o_plt(flask_aves_072821) +
  labs(title = "8 Day Dry Air Test")
```

8 and 10 are still problems, but 9 performed well. Flask 9 caused some pressure locking on the picarro. 

# 7 Dry Air test 
```{r}
data_082221 <- tbl %>% 
  filter (DATE == "2021-08-22") %>% 
    mutate(
      UTC = hms(TIME),
      UTC_full = with_tz(ymd_hms(paste(DATE, TIME)), tzone = "UTC"), 
      MDT = with_tz(UTC_full, tzone = "America/Denver"),
      seconds = row_number()
    ) %>% 
      filter(MDT > "2021-08-22 13:17:15" & MDT < "2021-08-22 14:34:10") %>% 
        outlet_batches()

waterConcentration_plt(data_082221)
outlet_batch_plt(data_082221)

manual_flasks_082221 <- data_082221 %>% 
  filter(MDT > "2021-08-22 13:37:15" & MDT < "2021-08-22 13:42:10") %>% 
  flask_ave_outlet() %>% 
  mutate(Flask = 6)

manual_flasks_082221 <-  manual_flasks_082221 %>% 
  bind_rows(
    data_082221 %>% 
      filter(MDT > "2021-08-22 14:27:15" & MDT < "2021-08-22 13:34:05") %>% 
        flask_ave_outlet() %>% 
          mutate(Flask = 16)
  )

flask_aves_082221 <- flask_ave_outlet(data_082221) %>% 
  mutate(Flask = c(2:5, 7:15)) %>% 
  bind_rows(manual_flasks_082221)

Flask_h2o_plt(flask_aves_082221)
```


# Two Week Water Vapor test 
## March 19, 2022, vapor in

Based on the H2O last three minutes plot, I felt that there were enough flasks where I needed to cut an extra 30 seconds off of the end than the function flask_last3minutes could do. So, I did that manually.

I compared the hand-done averages I did day-of with these calculated averages, and they all matched at better than 0.05 per mil. 
```{r}
data_031922 <- tbl %>% 
  filter(DATE == "2022-03-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-03-19 09:50:00" & MDT < "2022-03-19 14:07:00") %>% 
  h2o_batches()

waterConcentration_plt(data_031922)
h2o_batch_plt(data_031922)

h2o_LastThreeMinutes(data_031922)

flask_aves_0311922 <- data_031922 %>% 
    group_by(H2O_Batch) %>% 
      mutate( 
        row = row_number(),
        totalrows= n()
      ) %>% 
        filter (totalrows > 100) %>% 
          filter(row < (totalrows - 90)) %>% 
            filter(row > (totalrows - 330)) %>% 
              flask_out_ave() %>% 
          mutate(Flask = c(1:16))
```

## April 2, 2022 
```{r}
data_040222 <- tbl %>% 
  filter(DATE == "2022-04-02") %>% 
    BoulderTime() %>% 
      filter(MDT > "2022-04-02 12:38:00" & MDT < "2022-04-02 17:01:00") %>% 
        h2o_batches()  

waterConcentration_plt(data_040222)
h2o_batch_plt(data_040222)

h2O_FirstThreeMinutes(data_040222 %>% filter(H2O > 5000))

flask_aves_040222 <- data_040222 %>% 
  filter(H2O > 5000) %>% 
  flask_first3minutes() %>% 
  mutate(Flask = c(2:16))
```

## Differences
```{r}
WVtest_results <- flask_aves_0311922 %>% 
  left_join(flask_aves_040222, by = "Flask") %>% 
    mutate(
      d18O_diff = d18O_out.y - d18O_out.x,
      d2H_diff =   d2H_out.y - d2H_out.x
    )

WVtest_results_plt <- WVtest_results %>% 
  pivot_longer(cols = c(d18O_diff, d2H_diff)) %>% 
    mutate(
      # turn into ordered variable (factor) that keeps the order
      
      latex_name = as_factor(name) %>% fct_inorder()  %>% 
        # introduce latex substitutions
        fct_recode(
                   "$\\Delta \\delta^2H" = "d2H_diff",
                   "$\\Delta \\delta^{18}O" = "d18O_diff")
    ) %>% 
      ggplot()+
        aes(x = Flask, y = value, size = 2) +
        facet_wrap(~latex_name, labeller = latex_labeller, ncol = 1, scales = "free")+
        geom_point()+
        scale_x_continuous(breaks = c(2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
        theme_figure()+
        theme(
          legend.position = "none"
        )

print(WVtest_results_plt)
```



