---
title: "Seibert SWISS data"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---
# Set up 
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(dplyr)
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)
library(gridExtra)
library(egg)
library(readxl)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     as_tibble() %>%
#     dplyr::select(1, 2, 15, 17, 18, 19)   
# 
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# July 18 & July 19 data
SWISS: Toblerone. No data log from the microcontroller 

- 11, 12, 13 were 4th of July samples
- 8,9,10 were June 29th samples 
- 5,6,7 were June 24th samples
- 2,3,4 were June 19th samples 


## July 18 
Has two measurement periods, afternoon and evening 

I think you can see condensation in most of the measurements. I think this is a good argument that dead-end pull at such high concentrations doesn't work. 

flask 13 is messy  - averaging over a 9 minute window to represent real variability. Did a dead end pull to dry air at 30 ml/ min at 13:10. 

flask 11 - condensation has a problem 

March 20, 2023 note: adjust the filter by one hour to make the code work in pacific time zone, commented out the correct filter period
```{r}
#Filter data between 13:00 - 16:00 MDT 
data_071822_firstbatch <- tbl %>% 
  filter (DATE == "2022-07-18" | DATE == "2022-07-19") %>% 
  BoulderTime() %>% 
  #filter (MDT > "2022-07-18 13:00:00" & MDT < " 2022-07-18 16:00:00") %>% 
  filter (MDT > "2022-07-18 12:00:00" & MDT < " 2022-07-18 15:00:00") %>% 
  h2o_batches() 


flask13 <- data_071822_firstbatch %>% 
  #filter (MDT > "2022-07-18 13:09:00" & MDT < "2022-07-18 13:16:00") %>% 
  filter (MDT > "2022-07-18 12:09:00" & MDT < "2022-07-18 12:16:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 13,
        T = 23)

flask11 <-  data_071822_firstbatch %>% 
  #filter (MDT > "2022-07-18 13:52:00" & MDT < "2022-07-18 13:55:00") %>% 
  filter (MDT > "2022-07-18 12:52:00" & MDT < "2022-07-18 12:55:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 11,
         T = 25.0)


Flasks071822 <-  data_071822_firstbatch %>% 
  filter(H2O_Batch == 88 | H2O_Batch == 181 | H2O_Batch == 226 | H2O_Batch == 271) %>% 
  flask_first3minutes %>% 
  mutate(Flask = c(12,10,9,8),
         T = c(23.3, 23.0, 21.8, 23.2)) %>% 
  bind_rows(flask13, flask11) %>% 
  mutate(sampledate = ifelse(Flask > 10, "22-07-04", "22-06-29")) %>% 
  mutate(sampledepth = ifelse(Flask == 13 | Flask == 10, 75, 
                              ifelse(Flask == 12 | Flask == 9, 50, 25)))   
```

evening work  
March 20, 2023 note: adjust the filter by one hour to make the code work in pacific time zone, commented out the correct filter period
```{r}
data_071822_secondbatch <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
  BoulderTime() %>% 
  #filter (MDT > "2022-07-18 21:45:00" & MDT < " 2022-07-18 22:30:00") %>% 
  filter (MDT > "2022-07-18 20:45:00" & MDT < " 2022-07-18 21:30:00") %>% 
  h2o_batches() 

# waterConcentration_plt(data_071822_secondbatch)
# h2o_batch_plt(data_071822_secondbatch)
# 
# h2O_FirstThreeMinutes(data_071822_secondbatch)
# 
# d180_time_plt(data_071822_secondbatch)


flasks_2and3 <- data_071822_secondbatch %>% 
  filter(H2O_Batch == 31 | H2O_Batch == 74) %>% 
  flask_first3minutes() %>% 
  mutate (
    Flask = c(2,3),
    sampledate = c("22-06-19"),
    sampledepth = ifelse(Flask == 2, 25, 50),
    T = ifelse(Flask == 2, 24.2, 22)
  )
  

Flasks071822 <- Flasks071822 %>% bind_rows(flasks_2and3)
```

## July 19 

```{r}
data_071922 <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
  BoulderTime() %>% 
  #filter(MDT > "2022-07-19 11:00:00" & MDT < "2022-07-19 14:00:00") %>% 
  filter(MDT > "2022-07-19 10:00:00" & MDT < "2022-07-19 13:00:00") %>% 
  h2o_batches()  
  

# waterConcentration_plt(data_071922)
# d180_time_plt(data_071922)
# 
# h2o_batch_plt(data_071922)
# h2O_FirstThreeMinutes(data_071922)

flasks_071922 <- data_071922 %>% 
  filter(H2O_Batch == 58 | H2O_Batch == 111 | H2O_Batch == 179) %>% 
  flask_first3minutes() %>% 
  mutate(
    Flask = c(7,4,5),
    T = c(23,23,24.0),
    sampledate = ifelse(Flask > 4, "22-06-24", "22-06-19"),
    sampledepth = ifelse(Flask == 5, 25, 75)
    )

flask6 <- data_071922 %>% 
  #filter(MDT > "2022-07-19 13:48:00" & MDT < "2022-07-19 13:51:00") %>% 
  filter(MDT > "2022-07-19 12:48:00" & MDT < "2022-07-19 12:51:00") %>% 
  flask_out_ave() %>% 
  mutate(
    Flask = 6, 
    sampledate = "22-06-24",
    sampledepth = 50,
    T = 22.2
  )
  
flasks_071922 <- flasks_071922 %>% bind_rows(flask6)
```


## Correct Data & Save
```{r}
seibert_firstround <- Flasks071822 %>% bind_rows(flasks_071922)    %>% 
  mutate(
    #transfer to liquid values
    d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O_out,
    d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H_out,
    
    #transfer into VSMOW
    d18O_vsmow = (d18O_rothfuss - 0.7289) / 1.02,
    d2H_vsmow = (d2H_rothfuss - -.4987) / 1.0236,
    
    #apply SWISS offset correction
    d18o_offset = round((d18O_vsmow - 0.9),1),
    d2H_offset = round((d2H_vsmow - 2.6), 1),
    
    dexcess = d2H_offset - 8*d18o_offset
  )
  

seibert_firstround%>% 
  filter(sampledepth < 75) %>% 
  mutate(
    Site = "Seibert"
  ) %>% 
    dplyr::select(Site, sampledate, sampledepth, Flask, T, d18o_offset, SD_18O_out, d2H_offset, SD_2H_out) %>% 
      arrange(Flask) %>% 
        rename(Date = sampledate, Depth = sampledepth, AnalyticalError = SD_18O_out) %>% 
        write.csv("output/SeibertJulyData.csv")
```

## Plot 
### d18o
```{r}
seibert_d18o <- seibert_firstround %>% 
  #filter(sampledepth < 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Seibert, CO")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18o_offset - 0.9,
    ymin = d18o_offset + 0.9,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18o_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  #scale_shape_manual(values = c(22,23), name = "Sample Depth (cm)") +
  #scale_fill_manual(values = c("#441853", "#20908C"), name = "Sample Depth (cm)")+
  theme_figure()+
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )
  

print(seibert_d18o)
```



### d2H
```{r}
seibert_d2h <- seibert_firstround %>% 
  #filter(sampledepth < 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  # scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  # scale_fill_manual(values = c("#441853", "#20908C"), name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_blank(),
    #axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.position = "none",
    #legend.text = element_text(size = 14),
    #legend.title = element_text(size = 14)
  )

print(seibert_d2h)
```

### d-excess
```{r}

seibert_dexcess <- seibert_firstround %>% 
  #filter(sampledepth < 75) %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = dexcess + 3.5,
    ymin = dexcess - 3.5,
    width = 0
  )) + 
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  #scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  #scale_fill_manual(values = c("#441853", "#20908C"), name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(seibert_dexcess)
```






```{r Seibert July data}
ggarrange(seibert_d18o, seibert_d2h)
ggarrange(seibert_d18o, seibert_d2h, seibert_dexcess)
```

```{r}
crossplt <- seibert_firstround %>% 
  filter(sampledepth < 75) %>% 
  ggplot()+
    geom_abline(intercept = 10, slope = 8, size = 2, linetype = "longdash")+
  geom_errorbar(aes(
    x = d18o_offset,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = d2H_offset,
    xmax = d18o_offset - 0.9,
    xmin = d18o_offset + 0.9,
    height = 0)) +
  geom_point(
    aes(
      x = d18o_offset, 
      y = d2H_offset, 
      pch = factor(sampledepth),
      color = factor(sampledate)),
    size = 6
  )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  theme_figure()

crossplt
```

# September 2022 data
```{r}
Sept22 <- read_excel("data/Toblerone_Sept2022.xlsx")

Sept22 <- Sept22 %>% 
  mutate(
    sampledate = ymd(sampledate),
    T = c(16,15,14,18,18,18,19,19,20.5,17,18,19,21,22,21),
    d18O_rothfuss = 11.45 - 0.0795*T +1.0012*d18O,
    d2H_rothfuss =104.96 - 1.0342*T + 1.0724*d2H,
    
    d18O_vsmow = (d18O_rothfuss - 0.711) / 1.018,
    d2H_vsmow = (d2H_rothfuss - -0.4566) / 1.0297,
    
    d18o_offset =  round(d18O_vsmow - 0.9, 1),
    d2H_offset =  round(d2H_vsmow - 2.6,1),
    
    dexcess = d2H_offset - 8*d18o_offset
  )
```



On September 21, 2022 there was a large cold front that came in. At the time of sampling, dew point was 2-5°C below air temperature. 
```{r}
seibert_d18o_22 <- Sept22 %>% 
  filter(Exlude != TRUE) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O VSMOW$'))+
  ggtitle("Seibert, CO")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18o_offset - 1.0,
    ymin = d18o_offset + 1.0,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18o_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )
  

print(seibert_d18o_22)


seibert_d2h_22 <- Sept22 %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H VSMOW$'))+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_offset,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(seibert_d2h_22)


seibert_dexcess_22 <- Sept22 %>% 
  ggplot()+
  ylab("d-excess")+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = dexcess + 3.5,
    ymin = dexcess - 3.5,
    width = 0
  )) + 
  geom_point(
    aes(
      x= sampledate,
      y = dexcess,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 6
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)")+
  theme_figure()+
  #scale_y_continuous(breaks=c(-62, -58, -54))+
  theme(
    axis.text.x = element_text(size = 14, angle = 45,  hjust=1),
    axis.title.x = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14)
  )

print(seibert_dexcess_22)


ggarrange(seibert_d18o_22,seibert_d2h_22)
```

```{r}
seibert_firstround$sampledate <- as.Date(seibert_firstround$sampledate)

allseibert <- bind_rows(seibert_firstround, Sept22)

crossplt_all <- allseibert %>% 
  #get rid of bad 75 cm samples from June
  filter(d18o_offset<0) %>% 
  filter(d18o_offset != -5.7) %>% 
  #these data are distinctly weird and occured on a cold day where dew point and air temp were close
  filter(sampledate != "2022-09-21") %>% 
  ggplot()+
    geom_abline(intercept = 10, slope = 8, size = 2, linetype = "longdash")+
  geom_errorbar(aes(
    x = d18o_offset,
    ymax = d2H_offset - 3.6,
    ymin = d2H_offset + 3.6,
    width = 0)) +
  geom_errorbarh(aes(
    y = d2H_offset,
    xmax = d18o_offset - 0.9,
    xmin = d18o_offset + 0.9,
    height = 0)) +
  geom_point(
    aes(
      x = d18o_offset, 
      y = d2H_offset, 
      pch = factor(sampledepth),
      color = factor(sampledate)),
    size = 6
  )+
  #scale_shape_manual(values = c(22, 23,24), name = "Sample Depth (cm)") +
  scale_color_viridis(discrete = TRUE, option = "magma", name = "Sample Date") +
  ylab(latex2exp::TeX('$\\delta^2H (VSMOW)$'))+
  xlab(latex2exp::TeX('$\\delta^{18}O (VSMOW)$')) +
  theme_figure()

crossplt_all


```

```{r}
finaltbl <- allseibert %>% 
  mutate(site = "Seibert") %>% 
  dplyr::select(
    site, 
    sampledate,
    sampledepth,
    d18o_offset,
    d2H_offset,
    dexcess
  ) %>% 
  rename(
    "Site" = site,
    "Sample Date" = sampledate,
    "Sample Depth (cm)" = sampledepth,
    "d18O (VSMOW)" = d18o_offset,
    "d2H (VSMOW)" = d2H_offset,
    "d-excess ()" = dexcess
  )

write.csv(finaltbl, "output/SeibertResults_ch3.csv")
```


