---
title: "Seibert SWISS data"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged # omit to disable paged data table output
    number_sections: yes # change to no for unnumbered sections
    toc: yes # change to no to disable table of contents
    toc_float: true # change to false to keep toc at the top
    toc_depth: 3 # change to specify which headings to include in toc
    code_folding: show # change to hide to hide code by default
editor_options:
  chunk_output_type: console
---
# Set up 
```{r setup, echo = TRUE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) 
library(dplyr)
library(latex2exp)
library(viridis)
library(data.table)
library (lubridate)
library(plotly)
library(fs)
library(gridExtra)

setwd("/Volumes/Havranek External Hard Drive /NSF EAR 2023385/QAQC_bySWISS/SWISS_QAQC/")

# source all relevant scripting files
source(file.path ("scripts", "plotting_functions.R"))
source(file.path ("scripts", "PicarroData_BreakUp.R"))
source(file.path ("scripts", "Rachels_custom_plots.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)

#load data
# tbl <-
#     list.files ("data/Data2022", pattern = "*.dat", recursive = T, full.names = T) %>%
#     map_df(~read_table2(.)) %>%
#     as_tibble() %>%
#     dplyr::select(1, 2, 15, 17, 18, 19)   
# 
# saveRDS(tbl, "data/2022Data.RDS")


tbl <- readRDS(file.path("data", "2021Data.RDS")) %>% 
  bind_rows(readRDS(file.path("data","2022Data.RDS")))
```

# July 18 & July 19 data
SWISS: Toblerone. No data log from the microcontroller 

- 11, 12, 13 were 4th of July samples
- 8,9,10 were June 29th samples 
- 5,6,7 were June 24th samples
- 2,3,4 were June 19th samples 


## July 18 
Has two measurement periods, afternoon and evening 

I think you can see condensation in most of the measurements. I think this is a good argument that dead-end pull at such high concentrations doesn't work. 

flask 13 is messy  - averaging over a 9 minute window to represent real variability. Did a dead end pull to dry air at 30 ml/ min at 13:10. 

flask 11 - condensation has a problem 
```{r}
data_071822_firstbatch <- tbl %>% 
  filter (DATE == "2022-07-18" | DATE == "2022-07-2") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-07-18 13:00:00" & MDT < " 2022-07-18 16:00:00") %>% 
  h2o_batches() 


flask13 <- data_071822_firstbatch %>% 
  filter (MDT > "2022-07-18 13:09:00" & MDT < "2022-07-18 13:16:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 13)

flask11 <-  data_071822_firstbatch %>% 
  filter (MDT > "2022-07-18 13:52:00" & MDT < "2022-07-18 13:55:00") %>% 
  flask_out_ave() %>% 
  mutate(Flask = 11)


Flasks071822 <-  data_071822_firstbatch %>% 
  filter(H2O_Batch == 88 | H2O_Batch == 181 | H2O_Batch == 226 | H2O_Batch == 271) %>% 
  flask_first3minutes %>% 
  mutate(Flask = c(12,10,9,8)) %>% 
  bind_rows(flask13, flask11) %>% 
  mutate(sampledate = ifelse(Flask > 10, "22-07-04", "22-06-29")) %>% 
  mutate(sampledepth = ifelse(Flask == 13 | Flask == 10, 75, 
                              ifelse(Flask == 12 | Flask == 9, 50, 25)))
```

evening work
```{r}
data_071822_secondbatch <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
  BoulderTime() %>% 
  filter (MDT > "2022-07-18 21:45:00" & MDT < " 2022-07-18 22:30:00") %>% 
  h2o_batches() 

# waterConcentration_plt(data_071822_secondbatch)
# h2o_batch_plt(data_071822_secondbatch)
# 
# h2O_FirstThreeMinutes(data_071822_secondbatch)
# 
# d180_time_plt(data_071822_secondbatch)


flasks_2and3 <- data_071822_secondbatch %>% 
  filter(H2O_Batch == 31 | H2O_Batch == 74) %>% 
  flask_first3minutes() %>% 
  mutate (
    Flask = c(2,3),
    sampledate = c("22-06-19"),
    sampledepth = ifelse(Flask == 2, 25, 50)
  )
  

Flasks071822 <- Flasks071822 %>% bind_rows(flasks_2and3)
```

## July 19 

```{r}
data_071922 <- tbl %>% 
  filter (DATE == "2022-07-19") %>% 
  BoulderTime() %>% 
  filter(MDT > "2022-07-19 11:00:00" & MDT < "2022-07-19 14:00:00") %>% 
  h2o_batches()  
  

# waterConcentration_plt(data_071922)
# d180_time_plt(data_071922)
# 
# h2o_batch_plt(data_071922)
# h2O_FirstThreeMinutes(data_071922)

flasks_071922 <- data_071922 %>% 
  filter(H2O_Batch == 58 | H2O_Batch == 111 | H2O_Batch == 179) %>% 
  flask_first3minutes() %>% 
  mutate(
    Flask = c(7,4,5),
    sampledate = ifelse(Flask > 4, "22-06-24", "22-06-19"),
    sampledepth = ifelse(Flask == 5, 25, 75)
    )

flask6 <- data_071922 %>% 
  filter(MDT > "2022-07-19 13:48:00" & MDT < "2022-07-19 13:51:00") %>% 
  flask_out_ave() %>% 
  mutate(
    Flask = 6, 
    sampledate = "22-06-24",
    sampledepth = 50
  )
  
flasks_071922 <- flasks_071922 %>% bind_rows(flask6)
```


all flasks
```{r}
seibert_firstround <- Flasks071822 %>% bind_rows(flasks_071922)  
  

seibert_d18o <- seibert_firstround %>% 
  filter(sampledepth < 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^{18}O$'))+
  ggtitle("Seibert")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d18O_out - 0.5,
    ymin = d18O_out + 0.5,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d18O_out,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 3
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure()+
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_blank())
  

print(seibert_d18o)
```

```{r}
seibert_d2h <- seibert_firstround %>% 
  filter(sampledepth < 75) %>% 
  ggplot()+
  ylab(latex2exp::TeX('$\\delta^2H$'))+
  xlab("Sample Date")+
  geom_errorbar(aes(
    x = sampledate,
    ymax = d2H_out - 2.0,
    ymin = d2H_out + 2.0,
    width = 0)) +
  geom_point(
    aes(
      x= sampledate,
      y = d2H_out,
      pch = as.factor(sampledepth),
      fill = as.factor(sampledepth)
    ),
    size = 3
  ) +
  scale_shape_manual(values = c(22,23,24), name = "Sample Depth (cm)") +
  scale_fill_viridis(discrete = TRUE, name = "Sample Depth (cm)") +
  theme_figure()+
  theme(legend.title = element_text(size = 14),
        legend.text = element_text(size = 14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_blank())

print(seibert_d2h)
```

```{r Seibert July data}
grid.arrange(seibert_d18o, seibert_d2h, nrow = 2)
```



